\documentclass[a4paper]{article}

\input{C:/Users/liula/Desktop/Latex/Headers V1.2.tex}

\pagestyle{fancy}
\fancyhf{}
\rhead{Labix}
\lhead{Higher Category Theory}
\rfoot{\thepage}

\title{Higher Category Theory}

\author{Labix}

\date{\today}
\begin{document}
\maketitle
\begin{abstract}
\begin{itemize}
\end{itemize}
\end{abstract}
\pagebreak
\tableofcontents

\pagebreak
\section{Introduction to Infinity Categories}
\subsection{Infinity Categories as Simplicial Sets}
We recall some basic facts about simplicial sets. If $S:\Delta\to\bold{Set}$ is a simplicial set, then by Yoneda's emebdding we know that the $n$-simplices of $S$ are given by $$S([n])=\Hom_\bold{sSet}(\Delta^n,S)$$ In other words, specifying an $n$-simplex is the same as specifying a map of simplicial sets $$\Delta^n\to S$$



The foundations of infinity categories lay on the simpicial sets. Intuitively, any face $\partial_k\Delta$ of an $n$-simplex $\Delta$ captures a homotopy of the faces of $\partial_k\Delta$. 

\begin{defn}{Infinity Categories}{} An infinity category is a simplicial set $C$ such that each inner horn admits a filler. In other words, for all $0<i<n$, the following diagram commutes: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\Lambda_i^n} & C \\
	{\Delta^n}
	\arrow["\forall", from=1-1, to=1-2]
	\arrow[hook, from=1-1, to=2-1]
	\arrow["\exists"', dashed, from=2-1, to=1-2]
\end{tikzcd}}\\~\\
\end{defn}

\begin{defn}{Objects and Morphisms}{} Let $\mC$ be an infinity category. Define the following notions for $\mC$. 
\begin{itemize}
\item Define the objects of $\mC$ to be the $0$-simplices of $\mC$. 
\item Define the morphisms of $\mC$ to be the $1$-simplices of $\mC$. 
\end{itemize}
\end{defn}

\begin{defn}{Functors}{} Let $\mC,\mD$ be infinity categories. A functor from $\mC$ to $\mD$ is a morphism $F:\mC\to\mD$ of simplicial sets. 
\end{defn}

\begin{defn}{The Category of Infinity Categories}{} Define the category $\infty\bold{-Cat}$ of infinity categories to be the full subcategory of $\bold{sSet}$ consisting of infinity categories. 
\end{defn}

\begin{lmm}{}{} Let $\mC,\mD$ be infinity categories. Let $F:\mC\to\mD$ be a functor. Then the following are true. 
\begin{itemize}
\item $F$ sends an object of $\mC$ to an object of $\mD$. 
\item $F$ sends a morphism in $\mC$ to a morphism in $\mD$. 
\item $F$ sends the identity morphism of $X\in\mC$ to the identity morphism of $F(X)\in\mD$. 
\item If $f:X\to Y$ and $g:Y\to Z$ are morphisms in $\mC$, then $F(g\circ f)=F(g)\circ F(f)$
\end{itemize}
\end{lmm}

Explicitly, morphisms of infinity categories behave exactly what we want it to be like: A generalization of functors between ordinary categories. However, note that it is not enough to specify a morphism of infinity categories just from specifying it on objects. This is because we also need to tell the functor where to map the $n$-simplices. In other words, we need to tell the functor where to send the homotopy data. 

\begin{prp}{}{} Let $\mC$ be a category. Then the nerve $N_\bullet(\mC)$ of $\mC$ is an infinity category. 
\end{prp}

In other words, the nerve functor $N_\bullet(-)$ actually lands in $N_\bullet$. 

\begin{prp}{}{} The nerve functor $N_\bullet:\bold{Cat}\to\infty\bold{-Cat}$ is fully faithful. This means that there is a bijection $$\{\text{Functors from }\mC\text{ to }\mD\}\;\;\overset{1:1}{\longleftrightarrow}\;\;\{\text{Functors from}N_\bullet(\mC)\text{ to }N_\bullet(\mD)\}$$ given by $N_\bullet$. 
\end{prp}

Recall that $\bold{sSet}$ is closed monoidal. Moreover, we can identify functors from two infinity categories $\mC$ to $\mD$ as the zero simplicies of the simplicial set $\Hom_\bold{sSet}(\mC,\mD)$ defined by $$[n]\mapsto\Hom\bold{sSet}(\mC\times\Delta^n,\mD)$$

In fact, we can show that $\Hom_\bold{sSet}(\mC,\mD)$ is an infinity category. 

\begin{prp}{}{} Let $\mC,\mD$ be infinity categories. Then $$\text{Hom}_\bold{sSet}(\mC,\mD)$$ is an infinity category. 
\end{prp}

\subsection{Natural Transformations}
\begin{defn}{Natural Transformations}{} Let $\mC,\mD$ be infinity categories. Let $F,G:\mC\to\mD$ be functors. A natural transformation from $F$ to $G$ is a morphism $\mC\times\Delta^1\to\mD$ such that the following diagram commutes: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\mC} & {\mC\times\Delta^1} & {\mC} \\
	\\
	& \mD
	\arrow["{\text{id}_\mC\times\delta_0}", from=1-1, to=1-2]
	\arrow["f"', from=1-1, to=3-2]
	\arrow["{\exists\eta}"{description}, dashed, from=1-2, to=3-2]
	\arrow["{\text{id}_\mC\times\delta_1}"', from=1-3, to=1-2]
	\arrow["g", from=1-3, to=3-2]
\end{tikzcd}}\\~\\
\end{defn}

\begin{lmm}{}{} Let $\mC,\mD$ be infinity categories. Let $F,G\in\Hom_\bold{sSet}(\mC,\mD)$ be functors. Then the following are equivalent. 
\begin{itemize}
\item $\eta:\mC\times\Delta^1\to\mD$ is a natural transformation from $F$ to $G$
\item $\eta$ is an $1$-simplex in $\Hom_\bold{sSet}(\mC,\mD)$. 
\item $\eta$ is a homotopy from $F$ to $G$. 
\end{itemize}
\end{lmm}

\begin{lmm}{}{} Let $\mC,\mD$ be categories. Let $F,G:\mC\to\mD$ be functors. Then $\alpha:F\Rightarrow G$ is a natural transformation if and only if $N(\alpha):N(\mC)\to N(\mD)$ is a natural transformation of infinity categories. 
\end{lmm}

\begin{defn}{Natural Isomorphisms}{} Let $\mC,\mD$ be infinity categories. Let $F,G:\mC\to\mD$ be functors. We say that $F$ and $G$ are naturally isomorphic if 
\end{defn}

\subsection{The Homotopy Category of Infinite Categories}
\begin{defn}{Homotopic Morphisms}{} Let $\mC$ be an infinity category. Two morphisms $f,g:C\to D$ are said to be homotopic if there exists a $2$-simplex $\sigma$ in $\mC$ such that 
\begin{itemize}
\item $d_0(\sigma)=\text{id}_D$
\item $d_1(\sigma)=g$
\item $d_2(\sigma)=f$
\end{itemize}
In this case we write $f\simeq g$. 
\end{defn}

Pictorially, we denote the existence of such a $\sigma$ by \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	& D \\
	& \sigma \\
	C && D
	\arrow["{\text{id}_D}", from=1-2, to=3-3]
	\arrow["f", from=3-1, to=1-2]
	\arrow["g"', from=3-1, to=3-3]
\end{tikzcd}}\\~\\

This diagram here does not denote commutative, but instead denotes the existence of a $2$-simplex $\sigma$ that has the above as vertices and edges. Rewriting the above definition, we can say that $g\circ f:C\to E$ is homotopic to $h:C\to E$ if there exists a $2$-simplex of the form \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	& D \\
	& \sigma \\
	C && E
	\arrow["g", from=1-2, to=3-3]
	\arrow["f", from=3-1, to=1-2]
	\arrow["h"', from=3-1, to=3-3]
\end{tikzcd}}\\~\\
By definition of an infinity category, every inner horn admits a filler. This means that for any composable morphisms $f$ and $g$ giving $g\circ f$, we can always find a morphism $h$ such that $g\circ f$ is homotopic to $h$. However, this $h$ may not be unique, so we cannot conclude that infinity categories have a well defined notion of composition. 

\begin{lmm}{}{} Let $\mC$ be an infinity category. Then the relation of homotopic between morphisms is an equivalence relation. 
\end{lmm}

QUESTION: IS THE FOLLOWING TRUE (Kerodon 1.4.3.7)

\begin{prp}{}{} Let $\mC$ be an infinity category. Let $f,g:X\to Y$ be morphisms in $\mC$. Then $f$ and $g$ are homotopic if and only if $\Delta^1\overset{f,g}{\longrightarrow}\mC$ are homotopic as morphisms of simplicial sets. 
\end{prp}

\begin{prp}{}{} Let $C$ be an infinity category. Let $f,f':C\to D$ and $g,g':D\to E$ be morphisms in $C$. If $f\simeq f'$ and $g\simeq g'$, then $$g\circ f\simeq g'\circ f'$$
\end{prp}

We can explicitly write out the homotopy category of an infinity category as follows. 

\begin{prp}{}{} Let $\mC$ be an infinity category. Then the homotopy category $h(\mC)$ is isomorphic (as categories) to the category defined as follows. 
\begin{itemize}
\item The objects of $h(\mC)$ are the objects of $\mC$
\item For $A,B\in\mC$ two objects, the morphisms are the equivalence classes of morphisms $[f]$ for $f\in\Hom_\mC(A,B)$. 
\item Composition is defined by $$[g]\circ[f]=[g\circ f]$$ which is well defined by .2
\end{itemize}
\end{prp}

\begin{defn}{Isomorphisms in Infinity Categories}{} Let $\mC$ be an infinity category. Let $f:X\to Y$ be a morphism in $\mC$. We say that $f$ is an isomorphism if $[f]$ is an isomorphism in $h(\mC)$. Equivalently, $f$ is an isomorphism if there exists a morphism $g:Y\to X$ such that $g\circ f\simeq\text{id}_X$ and $f\circ g\simeq\text{id}_Y$. 
\end{defn}

Because the data of a functor between infinity categories carry $2$-simplicies to $2$-simplicies, we can easily deduce the following. 

\begin{lmm}{}{} Let $\mC,\mD$ be infinity category. Let $F:\mC\to\mD$ be a functor. Then the following are true. 
\begin{itemize}
\item If $f\simeq g$ are homotopic in $\mC$, then $F(f)\simeq F(g)$ are homotopic in $\mD$. 
\item If $f$ is an isomorphism in $\mC$, then $F(f)$ is an isomorphism in $\mD$. 
\end{itemize}
\end{lmm}

When $\mC,\mD$ are ordinary categories, we can talk about diagrams of shape $\mC$ in $\mD$. This just means that we only care about the shape of $\mC$, and we consider this shape inside $\mD$. This was the foundations for limits and colimits of a category. We can also do this for infinity categories, but recall that a functor between infinity categories carries much more data than just the shape of the domain infinity category: it also carries homotopy information. \\

\subsection{Equivalence of Infinity Categories}
\begin{defn}{Natural Isomorphisms}{} Let $\mC,\mD$ be infinity categories. Let $F,G:\mC\to\mD$ be functors. Let $\eta$ be a natural transformation from $F$ to $G$. We say that $\eta$ is a natural isomorphism if $\eta$ is an isomorphism as a morphism in $\Hom_\bold{sSet}(\mC,\mD)$. \\~\\

We say that $F$ and $G$ are naturally isomorphic if there exists a natural isomorphism from $F$ to $G$. 
\end{defn}

Kerodon 4.4.4.1

\begin{defn}{Homotopy Inverses}{} Let $\mC,\mD$ be infinity categories. Let $F:\mC\to\mD$ an $G:\mC\to\mD$ be functors. We say that $G$ is a homotopy inverse of $F$ 
\begin{itemize}
\item $G\circ F$ is naturally isomorphic to $\text{id}_\mC$ in $\Hom_\bold{sSet}(\mC,\mC)$
\item $F\circ G$ is naturally isomorphic to $\text{id}_\mD$ in $\Hom_\bold{sSet}(\mD,\mD)$
\end{itemize}
\end{defn}

Kerodon 4.5.1.10

\begin{defn}{Equivalence of Infinity Categories}{} Let $\mC,\mD$ be infinity categories. Let $F:\mC\to\mD$ be a functor. We say that $F$ is an equivalence of infinity categories if $F$ admits a homotopy inverse. In this case, we say that $\mC$ and $\mD$ are equivalent. 
\end{defn}

Recall that two objects in an infinity category $\mC$ is isomorphic if they are isomorphic in $h(\mC)$ in the ordinary sense. In our case, this means that we consider $G\circ F$ and $\text{id}_\mC$ to be objects of the infinity category $\Hom_\bold{sSet}(\mC,\mC)$, and they are isomorphic if $[G\circ F]=[\text{id}_\mC]$. This is the same as saying that $G\circ F$ and $\text{id}_\mC$ are homotopic. (It is also the same as saying $\mC$ and $\mD$ are homotopy equivalent as simplicial sets)

\begin{lmm}{}{} Let $\mC,\mD$ be infinity categories. If $\mC$ and $\mD$ are naturally isomorphic, then $\mC$ and $\mD$ are equivalent. 
\end{lmm}

\begin{prp}{}{} Let $\mC,\mD$ be ordinary categories. Let $F:\mC\to\mD$ be functor. Then $F:\mC\to\mD$ induces an equivalence of categories if and only if $N(F):N(\mC)\to N(\mD)$ induces an equivalence of categories. 
\end{prp}

\begin{prp}{}{} Let $\mC,\mD$ be infinity categories. Let $F:\mC\to\mD$ be a functor. If $F$ is an equivalence of infinity categories, then $h(F):h(\mC)\to h(\mD)$ is an equivalence of ordinary categories. 
\end{prp}

\begin{prp}{}{} Let $\mC,\mD$ be infinity categories. Let $F:\mC\to\mD$ be a functor. Then $F$ is an equivalence of infinity categories if and only if $$F\circ -:\Hom_\bold{sSet}(K,\mC)\to\Hom_\bold{sSet}(K,\mD)$$ is an equivalence of infinity categories for all simplicial sets $K$. 
\end{prp}

\subsection{The Core of an Infinity Category}

\pagebreak
\section{Infinity Categorical Constructions}
\subsection{Joins and Slices}
We begin by rewriting the definition of a simplex category as follows. Instead of having distinguished names $[n]$ for the objects, we instead just think of the simplex category with objects as finite and totally ordered sets. Indeed any of these sets will be in bijection to $[n]$ for some $n\in\N$. This language will help us define the join. 

\begin{defn}{}{} Let $J$ be a finite and totally ordered set. A cut of $J$ consists of two subsets $I,I'\subseteq J$ such that $$J=I\amalg I'$$ and $i<i'$ for all $i\in I$ and $i'<I'$. 
\end{defn}

\begin{defn}{Joins}{} Let $X,Y$ be simplicial sets. Define the join of $X$ and $Y$ to be the simplicial set $X\ast Y$ as follows. 
\begin{itemize}
\item Denote $J\neq\emptyset$ any finite and totally ordered set. Define $$X\ast Y(J)=\coprod_{\substack{I\amalg I'=J\\i<i'\text{ for }i\in I,i'\in I'}}X(I)\times Y(I')\coprod_{I,I'\text{ cuts of }J}X(I)\times Y(I')$$ where by convention, $X(\emptyset)=Y(\emptyset)=\ast$. 
\item For two finite and totally ordered sets $J$ and $J'$ and a morphism $J\to J'$ preserving order, the map $$(X\ast Y)[J']\to(X\ast Y)[J]$$ is defined as follows. Let $K,K'$ be a cut of $J'$. Then $\alpha$ restricts to two well defined maps $$\alpha|_{\alpha^{-1}(K)}:\alpha^{-1}(K)\to K\;\;\;\;\text{ and }\;\;\;\;\alpha|_{\alpha^{-1}(K')}:\alpha^{-1}(K')\to K'$$ In particular these are order preserving, and each are morphisms in the simplex category $\Delta$. Thus this gives us a unique morphism $$X(K)\times X(K')\to X(\alpha^{-1}(K))\times X(\alpha^{-1}(K'))$$ By taking the product of these maps, we thus obtain a morphism $(X\ast Y)[J']\to(X\ast Y)[J]$, turning the above definition into a simplicial set. 
\end{itemize}
\end{defn}

Concrete examples: 
\begin{itemize}
\item When $J=[0]$, we have that 
\begin{align*}
(X\ast Y)[0]&=X[0]\times Y(\emptyset)\amalg X(\emptyset)\times Y[0]\\
&=X_0\amalg Y_0
\end{align*}
which means that the vertices of $X\ast Y$ are the vertices of $X$ and $Y$ combined disjointly. 
\item When $J=[1]$, we have that 
\begin{align*}
(X\ast Y)[1]&=X[1]\times Y(\emptyset)\amalg X(\{0\})\times Y(\{1\}) \amalg X(\emptyset)\times Y[1]\\
&=X_1\amalg X_0\times Y_0\amalg Y_1
\end{align*}
\end{itemize}

TBA: The join of ordinary categories. 

\begin{lmm}{}{} Let $X$ and $Y$ be simplicial sets. Then $N(X\ast Y)\cong N(X)\ast N(Y)$
\end{lmm}

TBA: functoriality of join

\begin{prp}{}{} Let $X,Y$ be simplicial sets. Then $X\ast Y$ is an infinity category if and only if $X$ and $Y$ are infinity categories. 
\end{prp}

Recall that the over category $\mC/X$ consists of pairs $(Y,f:Y\to X)$ and morphism are given by commutative diagrams. Let us rephrase the definition as follows. The over category is the unique category such that if $\mD$ is another category, there is a bijection $$\Hom_\bold{CAT}(\mD,\mC/X)\cong\Hom_X(\mD\ast[0],\mC)$$ where the right hand side indicates that we only consider morphisms $\mD\ast[0]\to\mC$ in which $[0]$ is mapped to $X$. This characterization is due to the fact that a morphism $[0]\to\mC$ is essentially a choice of object in $\mC$, in which case we choose to be $X$. 

\begin{defn}{Over Category for Infinity Categories}{} Let $K,X$ be simplicial sets. Let $f:K\to X$ be a map. Define the over category (which is a simplicial set) $$f/X:\Delta\to\bold{Set}$$ as follows. 
\begin{itemize}
\item For each $n$, we have $$(f/X)_n=\Hom_{K/\bold{sSet}}(K\ast\Delta^n,X)$$
\end{itemize}
\end{defn}

TBA: Adjunction of join and slice. 

\pagebreak
\section{The Joyal Model Structure}
\subsection{Weak Equivalences in the Joyal Structure}
\begin{defn}{Categorical Equivalence}{} Let $X,Y$ be simplicial sets. Let $F:X\to Y$ be a morphism. We say that $F$ is a categorical equivalence if the induced functor $$-\circ F:\Hom_\bold{sSet}(Y,\mC)\to\Hom_\bold{sSet}(X,\mC)$$ induces a bijection on isomorphism classes $$\pi_0\left(\Hom_\bold{sSet}(Y,\mC)^\simeq\right)\to\pi_0\left(\Hom_\bold{sSet}(X,\mC)^\simeq\right)$$
\end{defn}

Kerodon 4.5.3.1\\

Priori: what is $\Hom^\simeq$?? (Core??)

\begin{lmm}{}{} Let $\mC,\mD$ be infinity categories. Let $F:\mC\to\mD$ be a functor. Then $F$ is a categorical equivalence if and only if $F$ is an equivalence of infinity categories. 
\end{lmm}

\subsection{Homotopy Pullbacks and Pushouts}
Because the standard model structure on $\bold{sSet}$ and the Joyal model structure are not Quillen equivalent, there are differences also in homotopy limits and colimits. 

\begin{defn}{Homotopy Pullbacks}{} Let the following be a diagram of infinity categories and functors. \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\mC_0} & \mC & {\mC_1}
	\arrow["F", from=1-1, to=1-2]
	\arrow["G"', from=1-3, to=1-2]
\end{tikzcd}}\\~\\
Let $\text{Isom}(\mC)$ denote the full subcategory of $\Hom_\bold{sSet}(\Delta^1,\mC)$ consisting of isomorphisms. Define the homotopy limit of the diagram with respect to the Joyal structure to be the two times pullback $$\mC_0\times_\mC^{hJ}\mC_1=\mC_0\times_{\Hom_\bold{sSet}(\{0\},\mC)}\text{Isom}(\mC)\times_{\Hom_\bold{sSet}(\{1\},\mC)}\mC_1$$ Here we identify the vertices of $\Delta^1$ as $0$ and $1$, and we use the isomorphism $\mC\cong\Hom_\bold{sSet}(\Delta^0,\mC)$. 
\end{defn}

Kerodon 4.5.2.1

\pagebreak
\section{Simplicial Categories as Models for Infinity Categories}
\subsection{Simplicial Categories}
\begin{defn}{Simplicial Categories}{} A simplicial category $\mC$ is a category enriched over $\bold{sSet}$. Explicitly, it consists of the following data: 
\begin{itemize}
\item $\mC$ is a category (and so consisting of objects, morphisms that satisfy associativity and unitality)
\item For each $X,Y\in\mC$, $\Hom_\mC(X,Y)$ is a simplicial set. 
\item For each $XZ,Y,Z\in\mC$, the composition rule $$\circ:\Hom_\mC(Y,Z)\times\Hom_\mC(X,Y)\to\Hom_\mC(X,Z)$$ is a morphism of simplicial sets. 
\end{itemize}
These data are organized such that the following coherence diagrams are commutative: 
\begin{itemize}
\item Associativity: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\Hom_\mC(Z,W)\times\Hom_\mC(Y,Z)\times\Hom_\mC(X,Y)} & {\Hom_\mC(Z,W)\times\Hom_\mC(X,Z)} \\
	{\Hom_\mC(Y,W)\times\Hom_\mC(X,Y)} & {\Hom_\mC(X,W)}
	\arrow["{\text{id}\times\circ}", from=1-1, to=1-2]
	\arrow["{\circ\times\text{id}}"', from=1-1, to=2-1]
	\arrow["\circ", from=1-2, to=2-2]
	\arrow["\circ"', from=2-1, to=2-2]
\end{tikzcd}}\\~\\
\item Unitality: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\{\text{id}_Y\}\times\Hom_\mC(X,Y)} & {\Hom_\mC(X,Y)\times\{\text{id}_X\}} & {\Hom_\mC(X,Y)\times\Hom_\mC(X,X)} \\
	{\Hom_\mC(Y,Y)\times\Hom_\mC(X,Y)} & {\Hom_\mC(X,Y)} & {\Hom_\mC(X,Y)}
	\arrow[hook, from=1-1, to=2-1]
	\arrow["{\text{proj}}", from=1-1, to=2-2]
	\arrow[hook, from=1-2, to=1-3]
	\arrow["{\text{proj}}"', from=1-2, to=2-3]
	\arrow["\circ", from=1-3, to=2-3]
	\arrow["\circ"', from=2-1, to=2-2]
\end{tikzcd}}\\~\\
\end{itemize}
\end{defn}

Given an ordinary category, one can construct a simplicial category in which the the higher morphisms are trivial. 

\begin{defn}{The Constant Simplicial Category}{} Let $\mC$ be a category. Define a simplicial category $\underline{\mC}$ as follows. 
\begin{itemize}
\item The objects of $\underline{\mC}$ are the objects of $\mC$
\item For $X,Y\in\mC$, define $\Hom_{\underline{\mC}}X,Y)$ to be the simplicial set given by $$\Delta^\text{op}\to\{\Hom_\mC(X,Y)\}\hookrightarrow\bold{Set}$$
\item For $X,Y,Z\in\mC$, define the composition law $$\circ:\Hom_{\underline{\mC}}(Y,Z)\times\Hom_{\underline{\mC}}(X,Y)\to\Hom_{\underline{\mC}}(X,Z)$$ by the composition law $\Hom_\mC(Y,Z)\times\Hom_\mC(X,Y)\to\Hom_\mC(X,Z)$
\end{itemize}
\end{defn}

Conversely, if we start with a simplicial category, we can recover a family of ordinary categories. 

\begin{defn}{The Ordinary Categories Associated to a Simplicial Category}{} Let $\mC$ be a simplicial category. Let $n\in\N$. Define a category $\mC_n$ as follows. 
\begin{itemize}
\item The objects of $\mC_n$ are the objects of $\mC$
\item For $X,Y\in\mC_n$, the set of morphisms are given by $$\Hom_{\mC_n}(X,Y)=\left(\Hom_\mC(X,Y)\right)_n$$ are given by the $n$-simplicies of the simplicial set $\Hom_\mC(X,Y)$. In particular, the identity morphism is given by the $n$-simplex corresponding to the map $\Delta^n\to\Delta^0\overset{\text{id}_X}{\longrightarrow}\Hom_\mC(X,X)$
\item For $f:X\to Y$ and $g:Y\to Z$ two morphisms in $\mC_n$, the composition $g\circ f$ is given by the image of $(g,f)$ in the composition law $$\circ:\Hom_\mC(Y,Z)\times\Hom_\mC(X,Y)\to\Hom_\mC(X,Z)$$
\end{itemize}
\end{defn}

We call $\mC_0$ the underlying category of the simplicial category. Indeed, there is a forgetful functor that sends every simplicial category to its underlying category. (It should be adjoint to constant simplicial category?)

\begin{defn}{Simplicial Functors}{} Let $\mC,\mD$ be simplicial categories. Let $F:\mC\to\mD$ be a functor. We say that $F$ is a simplicial functor if the induced map $$F:\Hom_\mC(X,Y)\to\Hom_\mD(F(X),F(Y))$$ for each $X,Y\in\mC$ is a morphism of simplicial sets. 
\end{defn}

\begin{defn}{Simplicial Categories}{} Define the category of simplicial categories $$\bold{Cat}_\bold{sSet}$$ by the following data. 
\begin{itemize}
\item The objects are the simplicial categories
\item The morphisms are the simplicial functors
\item Composition is given by the usual composition of functors. 
\end{itemize}
\end{defn}

\begin{prp}{}{} Let $\mC$ be a category. Then $\mC$ is a simplicial category if and only if $\mC$ is a simplicial object in $\bold{Cat}$ such that the underlying simplicial set of objects is constant. 
\end{prp}

1.1.4.2 HTT

\begin{defn}{Weakly Equivalent Simplicial Categories}{} Let $\mC,\mD$ be simplicial categories. Let $F:\mC\to\mD$ be a simplicial functor. We say that $F$ is a weak equivalence if the following are true. 
\begin{itemize}
\item For all $A,B\in\mC$, the induced map of simplicial sets $$F:\Hom_\mC(A,B)\to\Hom_\mC(F(A),F(B))$$ is weakly equivalent. 
\item For all $D\in\mD$, there exists some $C\in\mC$ such that $F(C)\cong D$
\end{itemize}
\end{defn}

Note: Markus land says this is weak equivalence, HTT says that this equivalence. 

\subsection{The Homotopy Coherent Nerve}
\begin{defn}{Simplicial Path Category}{} Let $(P,\leq)$ be a partially ordered set. Define the simplicial path category $$\bold{Path}[P]$$ to consist of the following data. 
\begin{itemize}
\item The objects of $\bold{Path}[P]$ are the elements of $P$. 
\item Let $x,y\in P$ be objects. Define a partially ordered set $\bold{FinLin}(x,y)$ where elements are given by finite linearly ordered subsets $$\{x=x_0<\cdots<x_m=y\}\subseteq P$$ of $P$ with start point $x$ and end point $y$ and ordering given by reverse inclusion. Denote by the same name its associated category. Define the set of morphisms from $x$ to $y$ to be $$\Hom_{\bold{Path}[P]}(x,y)=N_\bullet\left(\bold{FinLin}(x,y)\right)$$ In particular, the identity morphism is $\text{id}_x\in\Hom_{\bold{Path}[P]}(x,x)$. 
\item Let $x,y,z\in P$ be objects. The composition law $$\circ\Hom_{\bold{Path}[P]}(y,z)\times\Hom_{\bold{Path}[P]}(x,y)\to\Hom_{\bold{Path}[P]}(x,z)$$ is given on vertices by $S\circ T=S\cup T$. 
\end{itemize}
\end{defn}

Note: the assignment $\Delta\to\bold{Path}[\Delta]$ defines a cosimplicial set given by $$[n]\mapsto\bold{Path}[\Delta^n]=\bold{Path}[n]$$

\begin{defn}{The Homotopy Coherent Nerve}{} Let $\mC$ be a simplicial category. Define the homotopy coherent nerve $$N_\bullet^\text{hc}(\mC):\Delta^\text{op}\to\bold{Set}$$ to be the simplicial set given at the $n$ level by $$[n]\mapsto\Hom_\bold{sSet}(\bold{Path}[n],\mC)$$
\end{defn}

By the Yoneda embedding, we obtain a natural isomorphism $$\Hom_\bold{sSet}(\Delta^n,N_\bullet^\text{hc}(\mC))\cong\Hom_\bold{sSet}(\bold{Path}[n],\mC)$$

\begin{defn}{The Homotopy Coherent Nerve Functor}{} Define the homotopy coherent nerve functor $$N_\bullet^\text{hc}:\bold{Cat}_\bold{sSet}\to\bold{sSet}$$ to consist of the following data. 
\begin{itemize}
\item For each simplicial category $\mC$, $N_\bullet ^\text{hc}(\mC)$ is the homotopy coherent nerve of $\mC$
\item For each simplicial functor $F:\mC\to\mD$, the morphism $$N_\bullet^\text{hc}(F):N_\bullet^\text{hc}(\mC)\to N_\bullet^\text{hc}(\mD)$$ is defined on the level of $n$ simplicies by $$\Hom_\bold{sSet}(\bold{Path}[n],\mC)\overset{F\circ -}{\longrightarrow}\Hom_\bold{sSet}(\bold{Path}[n],\mD)$$
\end{itemize}
\end{defn}

\begin{prp}{}{} Let $\mC$ be a simplicial category. Let $\mC_0$ denote the underlying ordinary category of $\mC$. Let $P$ be a partially ordered set. Let $\pi:\bold{Path}[P]\to\underline{P}$ be the simplicial functor given by the identity on objects. Then there is a monomorphism $$\{F\;|\;F:P\to\mC_0\text{ is a functor }\}\hookrightarrow\{G:\bold{Path}[P]\to\mC\}$$ given by sending an ordinary functor $F$ to the simplicial functor $$\bold{Path}[P]\overset{\pi}{\longrightarrow}P\overset{F}{\longrightarrow}\mC_0\hookrightarrow\mC$$
\end{prp}

\begin{lmm}{}{} Let $\mC$ be an ordinary category. Let $\underline{\mC}$ denote the constant simplicial category. Then there is an isomorphism of simplicial sets $$N_\bullet(\mC)\cong N_\bullet^\text{hc}(\underline{\mC})$$ induced by the above monomorphism. 
\end{lmm}

\begin{thm}{Cordier-Porter}{} Let $\mC$ be a simplicial category. If $\Hom_\mC(X,Y)$ is a Kan complex for all $X,Y\in\mC$, then $N_\bullet^\text{hc}(\mC)$ is an infinity category. 
\end{thm}

\subsection{The Comparison between Simplicial Categories and Infinity Categories}
\begin{defn}{The Generalized Path Category}{} Let $S$ be a simplicial set. Define the generalized path category of $S$ to be the limit $$\bold{Path}[S]_\bullet=\lim_{\Delta}\bold{Path}[-]$$ where $\bold{Path}[\Delta^n]=\bold{Path}[n]$. 
\end{defn}

Kerodon 2.4.4.3

\begin{thm}{The Nerve-Path Adjunction}{} The homotopy coherent nerve and the path category forms an adjunction $$\bold{Path}[-]_\bullet:\bold{sSet}\rightleftarrows\bold{Cat}_\bold{sSet}:N_\bullet^\text{hc}$$ Explicitly, this means that there is an isomorphism $$\Hom_{\bold{Cat}_\bold{sSet}}(\bold{Path}[S]_\bullet,\mC)\cong\Hom_\bold{sSet}(S,N_\bullet^\text{hc}(\mC))$$
\end{thm}

Infinity categorise are fibrant objects of the Joyal model structure. In order to show that simplicial categories also give a theory of infinity categories, we need to show that all of its homotopy data and constructions are equivalent. We show this using a Quillen equivalence type theorem. 

\subsection{The Infinity Category of Spaces}
\begin{defn}{The Category of Kan Complexes}{} Define the category of Kan complexes $$\bold{Kan}$$ to be the full subcategory of $\bold{sSet}$ consisting of Kan complexes. Explicitly, it consists of the following data. 
\begin{itemize}
\item The objects are the Kan complexes
\item For $X,Y$ two Kan complexes, a morphism $f:X\to Y$ is a morphism of simplicial sets
\item Composition is given by the composition of morphisms of simplicial sets
\end{itemize}
\end{defn}

\begin{lmm}{}{} The category $\bold{Kan}$ is a simplicial category. Moreover, $\Hom_\bold{Kan}(X,Y)$ is a Kan complex. 
\end{lmm}

Lurie def vs Dwyer-Kan def is different. 

\begin{defn}{$\infty$-Category of Spaces}{} Define the $\infty$-category of spaces to be the simplicial set $$\mS=N_\bullet^\text{hc}(\bold{Kan})$$
\end{defn}

\begin{lmm}{}{} The $\infty$-category of spaces $\mS$ is an $\infty$-category. 
\end{lmm}

Digression: We began with two pairs of adjoint functors in Simplicial Methods in Topology: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	& {\bold{Cat}} \\
	{\bold{sSet}} \\
	& {\bold{Top}}
	\arrow["{N_\bullet}", shift left, from=1-2, to=2-1]
	\arrow["h", shift left, from=2-1, to=1-2]
	\arrow["{\abs{\;\cdot\;}}", shift left, from=2-1, to=3-2]
	\arrow["{S_\bullet}", shift left, from=3-2, to=2-1]
\end{tikzcd}}\\~\\
We have introduced the notion of Kan complexes and $\infty$-categories, which are also simplicial sets. We also saw that the two pairs of adjunction descend to these special simplicial sets: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\bold{sSet}} \\
	\\
	{\infty-\bold{Cat}} && {\bold{Cat}} \\
	{\bold{Kan}} && {\bold{Top}}
	\arrow["{\text{full}}", hook, from=3-1, to=1-1]
	\arrow["h", shift left, from=3-1, to=3-3]
	\arrow["{N_\bullet}", shift left, from=3-3, to=3-1]
	\arrow["{\text{full}}", hook, from=4-1, to=3-1]
	\arrow["{\abs{\;\cdot\;}}", shift left, from=4-1, to=4-3]
	\arrow["{S_\bullet}", shift left, from=4-3, to=4-1]
\end{tikzcd}}\\~\\
Finally in the last section we introduced another pair of adjunction from simplicial categories. Together with the forgetful functor sending a simplicial category $\mC$ to $\mC_0$ we obtain: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\bold{sSet}} && {\bold{Cat}_\bold{sSet}} \\
	\\
	{\infty-\bold{Cat}} && {\bold{Cat}} \\
	{\bold{Kan}} && {\bold{Top}}
	\arrow["{\bold{Path}[-]_\bullet}", shift left, from=1-1, to=1-3]
	\arrow["{N_\bullet^\text{hc}}", shift left, from=1-3, to=1-1]
	\arrow["{\text{Forgetful}}", from=1-3, to=3-3]
	\arrow["{\text{full}}", hook, from=3-1, to=1-1]
	\arrow["{\text{Ho}}", shift left, from=3-1, to=3-3]
	\arrow["{N_\bullet}", shift left, from=3-3, to=3-1]
	\arrow["{\text{full}}", hook, from=4-1, to=3-1]
	\arrow["{\abs{\;\cdot\;}}", shift left, from=4-1, to=4-3]
	\arrow["{S_\bullet}", shift left, from=4-3, to=4-1]
\end{tikzcd}}\\~\\

\pagebreak
\section{Space of Morphisms between Vertices}
\subsection{The Mapping Spaces}
For an ordinary category $\mC$, we have the notion of Hom sets (at least for locally small categories). We would like to reproduce this notion for infinity categories. 

\begin{defn}{Mapping Spaces}{} Let $\mC$ be an infinity category. Let $x,y\in\mC$ be objects. Define the mapping space from $x$ to $y$ to be the homotopy pullback $$\Hom_\mC(x,y)=\{x\}\times_\mC^h\{y\}$$
\end{defn}

Recall that the homotopy pullback is defined to be an iterated pullback. Explicitly, we can write the mapping space as $$\Hom_\mC(x,y)=\{x\}\times_{\Hom_\bold{sSet}(\{0\},\mC)}\times\Hom_\bold{sSet}(\Delta^1,\mC)\times_{\Hom_\bold{sSet}(\{1\},\mC)}\{y\}$$

Note: Land 1.3.47, Kerodon 4.6\\

Recall that a an $n$-simplex $x$ is degenerate if any two of its consecutive vertices are given by the same element. Explicitly, this means that $x$ lies in the image of some degeneracy map $s_k$. 

\begin{defn}{The Right Mapping Space}{} Let $\mC$ be an infinity category. Let $x,y\in\mC$ be objects. Define the right mapping space from $x$ to $y$ to be the simplicial set defined by $$\Hom_\mC^R(x,y)([n])=\left\{h\in\mC_{n+1}\;\bigg{|}\;d_{n+1}(h)=(\underbrace{s_0\circ\cdots\circ s_0}_{n\text{ times}})(x)\text{ and }(d_0\circ\cdots\circ d_n)(h)=y\right\}$$ for each $n\in\N$. 
\end{defn}

In plain English, the hom set from $x$ to $y$ on the $n$th level consists of $n+1$-simplices $h$ for which the face of $h$ with the first $n$-vertices are given by the $n$ simplex $[x,\dots,x]$, while the last vertex of $h$ is given by $y$. 

\begin{defn}{The Left Mapping Space}{} Let $\mC$ be an infinity category. Let $x,y\in\mC$ be objects. Define the left mapping space from $x$ to $y$ to be the simplicial set defined by $$\Hom_\mC^L(x,y)([n])=\left\{h\in\mC_{n+1}\;\bigg{|}\;d_{n+1}(h)=(\underbrace{s_0\circ\cdots\circ s_0}_{n\text{ times}})(y)\text{ and }(d_0\circ\cdots\circ d_n)(h)=x\right\}$$ for each $n\in\N$. 
\end{defn}

These two notions are equivalent up to homotopy (Land) Also pullbacks (Land)

\begin{prp}{}{} Let $\mC$ be an infinity category. Let $x,y\in\mC$. Then both mapping spaces $\Hom_\mC^R(x,y)$ and $\Hom_\mC^L(x,y)$ are Kan complexes. 
\end{prp}

\begin{prp}{}{} Let $\mC$ be an infinity category. Let $x,y\in\mC$. Then the following are true. 
\begin{itemize}
\item The right mapping space is isomorphic to the pullback $$\Hom_\mC^R(x,y)\cong\{x\}\times_{\Hom_\bold{sSet}(\{0\},\mC)}\mC/y$$
\item The left mapping space is isomorphic to the pullback $$\Hom_\mC^L(x,y)\cong x/\mC\times_{\Hom_\bold{sSet}(\{1\},\mC)}\{y\}$$
\end{itemize}
\end{prp}

\subsection{Composition of Morphisms in Infinity Categories}
\begin{defn}{}{} Let $\mC$ be an infinity category. Let $x,y,z\in\mC$ be objects. Define the ??? $$\text{Map}_\mC(x,y,z)$$ of $x,y,z$ to be the pullback of the diagram: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	& {\Hom_\bold{sSet}(\Delta^2,\mC)} \\
	{\Delta^0} & {\Hom_\bold{sSet}(\Delta^0\times\Delta^0\times\Delta^0,\mC)\simeq\mC\times\mC\times\mC}
	\arrow[from=1-2, to=2-2]
	\arrow["{(x,y,z)}", from=2-1, to=2-2]
\end{tikzcd}}\\~\\
in $\bold{sSet}$, where the vertical map is given by the inclusion of each $\Delta^0$ to a vertex of $\Delta^2$. 
\end{defn}

Rewriting notation: $\text{Map}_\mC(x,y)=\Hom_\mC(x,y)$. 

\begin{lmm}{}{} Let $\mC$ be an infinity category. Let $x,y,z\in\mC$ be objects. Then the map \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\text{Map}_\mC(x,y,z)} & {\text{Map}_\mC(y,z)\times\text{Map}_\mC(x,y)}
	\arrow["{d_0\times d_2}", from=1-1, to=1-2]
\end{tikzcd}}\\~\\
is a trivial Kan fibration. 
\end{lmm}

\begin{defn}{Composition of Morphisms}{} Let $\mC$ be an infinity category. Let $x,y,z\in\mC$ be objects. Let $f:x\to y$ and $g:y\to z$ be morphisms in $\mC$. Define the composite of $f$ and $g$ to be the image of $(g,f)$ in the following: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\text{Map}_\mC(y,z)\times\text{Map}_\mC(x,y)} & {\text{Map}_\mC(x,y,z)} & {\text{Map}_\mC(x,z)}
	\arrow["k", from=1-1, to=1-2]
	\arrow["{d_1}", from=1-2, to=1-3]
\end{tikzcd}}\\~\\
where $k$ is a choice of the homotopy inverse of $d_0\times d_2:\text{Map}_\mC(x,y,z)\to\text{Map}_\mC(y,z)\times\text{Map}_\mC(x,y)$. 
\end{defn}

Upshot: Composition of morphisms are only well defined up to an equivalence class of homotopic maps. 

\pagebreak
\section{Limits and Colimits}
\subsection{Terminal and Initial Objects}
\begin{defn}{Initial and Terminal Objects}{} Let $\mC$ be an infinity category. Let $x\in\mC$ be an object. 
\begin{itemize}
\item We say that $x$ is initial if for all objects $y\in\mC$, there is a homotopy equivalence $$\Hom_\mC(x,y)\simeq\Delta^0$$
\item Dually, we say that $x$ is terminal if for all objects $y\in\mC$, there is a homotopy equivalence $$\Hom_\mC(y,x)\simeq\Delta^0$$
\end{itemize}
\end{defn}

\begin{prp}{}{} Let $\mC$ be an infinity category. Let $x\in\mC$ be an object. Then the following are equivalent. 
\begin{itemize}
\item $x$ is terminal. 
\item For all $n\geq 1$, every lifting problem of the form \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\Delta^{\{n\}}} & {\partial\Delta^n} & \mC \\
	& {\Delta^n}
	\arrow[hook, from=1-1, to=1-2]
	\arrow[from=1-2, to=1-3]
	\arrow["x", bend left = 20, from=1-1, to=1-3]
	\arrow[from=1-2, to=2-2]
	\arrow[dashed, from=2-2, to=1-3]
\end{tikzcd}}\\~\\
has a solution. 
\end{itemize}
\end{prp}

initial / terminal carries over by equivalence\\

initial in i-cat imply initial in hCat

\subsection{Limits and Colimits}
\begin{defn}{Functor of Constant Diagrams}{} Let $K$ be a simplicial set. Let $\mC$ be an infinity category. Define the functor of constant diagram $$\Delta:\mC\to\Hom_\bold{sSet}(K,\mC)$$ to be the morphism of simplicial sets defined by $$\mC_n\cong\Hom_\bold{sSet}(\Delta^n,\mC)\longrightarrow\Hom_\bold{sSet}(K\times\Delta^n,\mC)$$ induced by the projection map $K\times\Delta^n\to\Delta^n$. 
\end{defn}

In particular, notice that for $X\in\mC$ an object, $\Delta X$ is precisely the unique morphism from $K$ to the simplicial set $\{X\}$. 

\begin{defn}{Limits in Infinity Categories}{} Let $K,\mC$ be infinity categories. Let $F:K\to\mC$ be a morphism. We say that $X$ is the limit of $F$ exhibited by $u:\Delta X\Rightarrow F$ if for all $Z\in\mC$, the following composite: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{\Hom_\mC(X,Y)} & {\Hom_{\Hom_\bold{sSet}(K,\mC)}(\Delta X,\Delta Y)} & {\Hom_{\Hom_\bold{sSet}(K,\mC)}(\Delta X,F)}
	\arrow["\Delta", from=1-1, to=1-2]
	\arrow["{[u]\circ -}", from=1-2, to=1-3]
\end{tikzcd}}\\~\\
is a homotopy equivalence of simplicial sets. 
\end{defn}

TBA: If $K,\mC$ are nerves of ordinary category, then the above definition recovers the usual notion of limits. 

\subsection{Equivalent Formulations of the (Co)Limit}
\begin{prp}{}{} Let $K$ be a Kan complex. Let $\mC$ be an infinity category. Let $F:K\to\mC$ be a functor. Let $X\in\mC$ be an object. 
\begin{itemize}
\item $X$ the limit of $F$ exhibited by $u:\Delta X\Rightarrow F$ if and only if $u$ is the final object in $$\mC\times_{\Hom_\bold{sSet}(\{0\},\Hom_\bold{sSet}(K,\mC))}\Hom_\bold{sSet}(\Delta^1,\Hom_\bold{sSet}(K,\mC))\times_{\Hom_\bold{sSet}(\{1\},\Hom_\bold{sSet}(K,\mC))}\{u\}$$
\end{itemize}
\end{prp}


\pagebreak
\section{Relation to Model Categories}
\subsection{Inverting Morphisms in an Infinity Category}
\begin{defn}{}{} Let $\mC$ be an infinity category. Let $W$ be a collection of morphisms in $\mC$. Define the category $$\mC[W^{-1}]$$ together with its canonical functor $F:\mC\to\mC[W^{-1}]$ by the following universal property. \\~\\

For every infinity category $\mD$ together with a functor $G:\mC\to\mD$ such that $G(f)$ is an equivalence for $f\in W$, there exists a unique functor $H:\mC[W^{-1}]\to\mD$ such that the following diagram commutes: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	\mC & {\mC[W^{-1}]} \\
	& \mD
	\arrow["F", from=1-1, to=1-2]
	\arrow["G"', from=1-1, to=2-2]
	\arrow["{\exists!H}", dashed, from=1-2, to=2-2]
\end{tikzcd}}\\~\\
\end{defn}

\begin{prp}{}{} Let $\mC$ be an infinity category. Let $W$ be a collection of morphisms in $\mC$. Then $\mC[W^{-1}]$ exists and is unique up to equivalence of infinity categories. 
\end{prp}

Given a category $\mC$ with weak equivalences $\mW$, we now have a way to systematically construct an infinity category associated to $\mC$. Namely, $$(\mC,\mW)\mapsto N(\mC)[\mW^{-1}]$$

\subsection{Exhibiting a Model Category as an Infinity Category}
Up until now, we have two ways of associating different types of categories with its homotopy category. Namely, if $\mC$ is a model category, then we can associate to it the homotopy category $\text{Ho}(\mC)$. Similarly, if $\mD$ is an infinity category, we can also associate to it a homotopy category $\text{Ho}(\mD)$. This constructions are highly related. In particular, there is a functor sending every model category to an infinity category such that the most important notions such as homotopy limits and colimits coincide. \\

Recall that for a model category $\mC$, we denote the full subcategory spanned by cofibrant objects by $\mC_c$. 

\begin{defn}{}{} Let $(\mC,W)$ be a model category. Let $\mD$ be an infinity category. Let $F:N(\mC_c)\to\mD$ be a functor. We say that $F$ exhibits the underlying category $\mC$ as $\mD$ if the functor induces an equivalence of categories $$N(\mC_c)[W^{-1}]\simeq\mD$$
\end{defn}

Ref:1.3.4.20 HA

\begin{thm}{[Dwyer-Kan]}{} Let $(\mC,\mW)$ be a model category. ??? determines a map $N(\mC_c)\to N(\mC_{cf})$ that induces an equivalence of infinity categories $$N(\mC_c)[\mW^{-1}]\simeq N(\mC_{cf})$$
\end{thm}

TBA: Left Quillen equivalence implies equivalence of infinity categories. 

\subsection{}
Presentable iff $\mD\simeq N(\mC_cf)$ where $\mC$ is a combinatorial simplicial model category. 


\end{document}
