\documentclass[a4paper]{article}

\input{C:/Users/liula/Desktop/Latex/Headers V1.2.tex}

\pagestyle{fancy}
\fancyhf{}
\rhead{Labix}
\lhead{Algebraic K Theory}
\rfoot{\thepage}

\title{Algebraic K Theory}

\author{Labix}

\date{\today}
\begin{document}
\maketitle
\begin{abstract}
\end{abstract}
\pagebreak
\tableofcontents

\pagebreak
\section{The K${_0}$-Group}
\subsection{K${_0}$ of a Symmetric Monoidal Category}
\begin{defn}{The K${_0}$-Group of a Symmetric Monoidal Category}{} Let $(\mC,I,\oplus)$ be a symmetric monoidal category. Let $\mC^\text{iso}$ be the category consisting of isomorphism classes of objects, which is also an abelian monoid under the operation $\oplus$. Define the $K_0$ group of $\mC$ by the Grothendieck completion $$K_0(\mC,I,\oplus)=\left(\mC^\text{iso}\right)^{-1}\mC^\text{iso}$$
\end{defn}

\subsection{K${_0}$ of a Ring}
\begin{defn}{The Category of Projective Modules over a Ring}{} Let $R$ be a ring. Define the category $P(R)$ of projective modules over $R$ as follows. 
\begin{itemize}
\item The objects are projective modules $M$ over $R$
\item For two projective modules $M,N$ over $R$, a morphism $M\to N$ is just an $R$-module homomorphism. 
\item Composition is given by the composition of functions. 
\end{itemize}
\end{defn}

\begin{lmm}{}{} Let $R$ be a ring. Then the category $P(R)$ is a symmetric monoidal category with the distinguished object $R$ as an $R$-module and binary operator $\oplus:P(R)\times P(R)\to P(R)$ the direct sum. 
\end{lmm}

\begin{defn}{The K${_0}$-Group of a Ring}{} Let $R$ be a ring. Define the $K_0$-group of $R$ by the Grothendieck completion of the abelain monoid: $$K_0(R)=P(R)^{-1}P(R)=K_0(P(R),R,\oplus)$$
\end{defn}

\subsection{K${_0}$ of an Abelian Category}
\subsection{K${_0}$ of a Waldhaussen Category}

\pagebreak
\section{The K${_1}$-Group}
\subsection{K${_1}$ of a Ring}
\begin{defn}{The K${_1}$-Group of a Ring}{} Let $R$ be a ring. Define the $K_1$-group of $R$ to be the group $$K_1(R)=\frac{GL(R)}{[GL(R),GL(R)]}$$
\end{defn}

\begin{prp}{}{} Let $R$ and $S$ be two rings. Then there is an isomorphism $$K_1(R\times S)\cong K_1(R)\oplus K_1(S)$$
\end{prp}

\begin{prp}{}{} Let $R$ be a ring. Then there is an isomorphism $$K_1(R)\cong K_1(M_n(R))$$ for any $n\in\N$. 
\end{prp}

\subsection{The Fundamental Theorems for K${_1}$ and K${_0}$}

\pagebreak
\section{The Negative K-Groups}

\pagebreak
\section{The K${_2}$-Group}
\subsection{The Steinberg Group}
\begin{defn}{The $n$th Steinberg Group}{} Let $R$ be a ring. For $n\geq 3$, define the $n$th Steinberg group by $$\text{St}_n(R)=\frac{\langle x_{ij}(r)\text{ for }r\in R, 1\leq i,j\leq n\rangle}{R}$$ where $R$ is the relation generated by 
\begin{itemize}
\item For $r,s\in R$, $x_{ij}(r)x_{ij}(s)=x_{ij}(rs)$ for $1\leq i,j\leq n$
\item For $r,s\in R$, $$[x_{ij}(r),x_{kl}(s)]=\begin{cases}
1 & \text{ if } j\neq k\text{ and }i\neq l\\
x_{il}(rs) & \text{ if } j=k \text{ and }i\neq l\\
x_{kj}(-rs) & \text{ if } j\neq k\text{ and }i=l
\end{cases}$$
\end{itemize}
\end{defn}

\begin{lmm}{}{} Let $R$ be a ring. For any $n\geq 3$, the $n$th Steinberg group $\text{St}_n(R)$ of $R$ includes into the $(n+1)$th Steinberg group $\text{St}_{n+1}(R)$. 
\end{lmm}

\begin{prp}{}{} Let $R$ be a ring. Let $n\geq 3$. Then the universal property of free groups with relations induce a canonical group surjection $$\phi_n:\text{St}_n(R)\to[GL(R),GL(R)]$$ that sends $x_{ij}(r)$ to $e_{ij}(r)$. 
\end{prp}

\begin{defn}{The Steinberg Group of a Ring}{} Let $R$ be a ring. Define the Steinberg group of $R$ by the direct limit $$\text{St}(R)=\varinjlim_{n\in\N\setminus\{0,1,2\}}\text{St}_n(R)$$
\end{defn}

\begin{prp}{}{} Let $R$ be a ring. The universal property of the direct limit induces a canonical group surjection $$\phi:\text{St}(R)\to[GL(R),GL(R)]$$
\end{prp}

\subsection{K${_2}$ of a Ring}
\begin{defn}{The K${_2}$-Group of a Ring}{} Let $R$ be a ring. Define the $K_2$-group of $R$ to be the kernel $$K_2(R)=\ker\left(\phi:\text{St}(R)\to[GL(R),GL(R)]\right)$$
\end{defn}

\begin{lmm}{}{} Let $R$ be a ring. Then there is an exact sequence of groups \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	0 & {K_2(R)} & {\text{St}(R)} & {[GL(R),GL(R)]} & {K_1(R)} & 0
	\arrow[from=1-1, to=1-2]
	\arrow[from=1-2, to=1-3]
	\arrow[from=1-3, to=1-4]
	\arrow[from=1-4, to=1-5]
	\arrow[from=1-5, to=1-6]
\end{tikzcd}}\\~\\
\end{lmm}

\begin{thm}{(Stein)}{} For any ring $R$, the $K_2$-group $K_2(R)$ is an abelian group. Moreover, we have $$Z(\text{St}(R))=K_2(R)$$
\end{thm}

\pagebreak
\section{The K${_n}$-Group}
\subsection{Universal Definition}
\begin{defn}{The Plus Construction}{} Let $R$ be a ring. Define $BGL(R)^+$ to be any CW complex that has a distinguished map $BGL(R)\to BGL(R)^+$ such that the following are true. 
\begin{itemize}
\item There is an isomorphism $\pi_1(BGL(R)^+)\cong K_1(R)$ given by the induced map $\pi_1(BGL(R))\to\pi_1(BGL(R)^+)$, which is required to be surjective with kernel $[GL(R),GL(R)]$
\item For each $n\in\N$, there are isomorphisms $$H_n(BGL(R);M)\cong H_n(BGL(R)^+;M)$$ for any $R$-module $M$. 
\end{itemize}
\end{defn}

Intuitively, $BGL(R)^+$ is a modification of the classifying space of $GL(R)$ so that their homology remains the same while its fundamental group returns $K_1(R)$. The latter point is important because $K_n$ will be defined as the $n$th homotopy group. 

\begin{defn}{K${_n}$ of a Ring}{} Let $R$ be a ring. Define the $n$th $K$-group of $R$ to be $$K_n(R)=\pi_n(BGL(R)^+)$$ for $n\geq 1$. 
\end{defn}

Notice that $BGL(R)^+$ for a ring $R$ is not defined uniquely. However, we can prove that any two such plus constructions are homotopy equivalent so that $K_n(R)$ is well defined. \\~\\

In order to accommodate the $0$th $K$-group, we make the following amendments. 

\begin{defn}{K-Theory of a Ring}{} Let $R$ be a ring. Define the $K$-theory of $R$ by $$K(R)=K_0(R)\times BGL(R)^+$$ so that $\pi_n(BGL(R)^+)=K_n(R)$ for all $n\geq 0$. 
\end{defn}

\section{}
\subsection{}
\begin{thm}{Serre-Swan Theorem I}{} Let $M$ be a smooth manifold. Let $E$ be a smooth vector bundle over $M$. Then the space of smooth sections $\Gamma(E)$ of $E$ is finitely generated and projective over $C^\infty(M)$. \\~\\

If $M$ is connected, then the space of smooth section is one-to-one with the finitely generated and projective modules over $C^\infty(M)$. 
\end{thm}

\begin{thm}{}{} Let $M$ be a smooth and connected manifold. Then the category of smooth vector bundles $\text{SVect}(M)$ is equivalent to the category of finitely generated projective modules $\text{FinProj}{_{C^\infty(M)}\text{Mod}}$ via the global section functor $$\Gamma:\text{SVect}(M)\to\text{FinProj}{_{C^\infty(M)}\text{Mod}}$$ defined by $E\mapsto\Gamma(E)$
\end{thm}

\subsection{}










\end{document}
