\documentclass[a4paper]{article}

\input{C:/Users/liula/Desktop/Latex/Headers V1.2.tex}

\pagestyle{fancy}
\fancyhf{}
\rhead{Labix}
\lhead{Algebraic Topology 3}
\rfoot{\thepage}

\title{Algebraic Topology 3}

\author{Labix}

\date{\today}
\begin{document}
\maketitle
\begin{abstract}
Algebraic Topology 3 picks up from Algebraic Topology 2 and defines the final invariant for homotopy equivalence called the homotopy groups. We shall see that such homotopy groups is a complete invariant for CW-complexes up to homotopy equivalence. CW-complexes also benefit from the homotopy groups with the homotopy analogue of excision and a unique new theorem called the suspension theorem that implies stability of the homotopy groups. \\~\\

The notes will then take a break from homotopy theory and redefine all the concepts (and some new ones) in the language of category theory. The point is that by looking into the picture, it is hoped that readers are able to understand how everything from Algebraic Topology 1-3 piece together into a coherent story. \\~\\

Equipped with categorical constructions, we are then ready to tackle on the covering space analogue for higher homotopy groups called fibrations. They will provide a long exact sequence for computations of higher homotopy groups. However, fibrations are not just useful for understanding the higher homotopy groups. They serve as the fundamental object of study in general topology, as well as algebraic topology. \\~\\

Finally, we will once again delve into a categorical setting and discuss a generalization of the fundamental group using category theory. Such a generalization also gives the full picture of how covering spaces interact with the fundamental group, as well as proving a more general version of Seifert-van Kampen theorem that now works when the intersection is not connected. \\~\\

In the last chapter, we will put both homology and cohomology into a general framework, and define axioms that ensure that homology and cohomology as an invariant is unique up to having properties such as excision. It will also pave way to stable homotopy theory, of which one important theorem called Brown's representability theorem states that cohomology theories and spectra (object of study in stable homotopy theory) determines each other in a functorial way. 
\end{abstract}
~\\~\\
References: 
\begin{itemize}
\item Notes on Algebraic Topology by Oscar Randal-Williams: \\
The first chapter gives a complete treatment of the first three sections of these notes, as well as providing the importance of fibrations on the higher homotopy groups. These notes are highly recommended to understanding the first three sections. 

\item Algebraic Topology by Allen Hatcher: \\
A more or less complete dictionary on all topics of these notes. However it is prone to the same problem in the sense that Hatcher's book is rather terse and definitions and parts of some theorems are scattered throughout the paragraphs rather than having a complete statement for reference. Nevertheless it is still the standard reference of the notes, albeit organized in a slightly different way. 

\item A non-visual proof that higher homotopy groups are abelian by Shintaro Fushida-Hardy: \\
This short piece of article proves that the higher homotopy groups are abelian in a purely algebraic way. Most geometric visualization of such a proof has the same underlying idea as the algebraic method. 
\end{itemize}

\pagebreak
\tableofcontents

\pagebreak

\section{The Higher Homotopy Groups}
The journey of Algebraic Topology began with the fundamental group, where we assigned a group to every space functorially. The notion of fundamental group heavily involves the notion of homotopy and therefore is heavily related to the notion of homotopy. However, one realizes that even with Seifert-van Kampen theorem and the theory of covering spaces, it is not easy to compute the fundamental group of a space. This is party, but not wholly due to the fundamental group is in general not abelian. If we instead work in an abelian setting, one is able to distinguish two non-isomorphic groups simply by analysing the torsion subgroups. Therefore we refine the concept of the fundamental group and procured the notion of homology and cohomology. Both functorial invariants now produce graded abelian groups for each space, one for each dimension $n\in\N$. In the case of cohomology, there is a canonical ring structure on cohomology that interacts with the topology of the underlying space. \\~\\

Now we turn to the final main invariant of topological spaces. The homotopy groups $\pi_n(X,x_0)$ serves as both a generalization of the fundamental group $\pi_1(X,x_0)$ in higher dimensions and a homotopic analogue to homology via the Hurewicz homomorphism $$h:\pi_n(X)\to H_n(X)$$ It is a strong invariant that is closely related to the notion of homotopy, all the while having mostly abelian groups as its output. The trade off is that the homotopy groups are very hard to compute. Such trade off has led to the blossoming of Algebraic Topology in its fullest. For instance, stable homotopy theory stems from a crucial fact called the Freudenthal suspension theorem, which states that such a sequence $$\pi_n(X)\to\pi_{n+1}(\Sigma X)\to\cdots$$ eventually stabilizes for large enough $n$. \\~\\

In this chapter we will closely study the $n$th homotopy groups such as its properties and develop tools to compute them. 

\subsection{The nth Homotopy Groups}
We begin not with the definition of the homotopy groups, but rather a slight generalization of pointed spaces and maps between them. 

\begin{defn}{Pairs of Space}{} Let $X$ be a topological space. A pair of space is a pair $(X,A)$ where $A\subseteq X$ is a subspace of $X$. A map of pairs $f:(X,A)\to(Y,B)$ is a continuous map $f:X\to Y$ such that $f(A)\subseteq B$. 
\end{defn}

\begin{defn}{Homotopy between Maps of Pairs}{} Let $f,g:(X,A)\to (Y,B)$ be maps of pairs. A homotopy between $f$ and $g$ is a homotopy $H:X\times[0,1]\to Y$ such that $H(A\times[0,1])\subseteq B$. 
\end{defn}

\begin{defn}{The nth Homotopy Groups}{} Let $(X,x_0)$ be a pointed space. Define the $n$th homotopy group $\pi_n(X,x_0)$ to be $$\pi_n(X,x_0)=\frac{\left\{\gamma:\left(I^n,\partial I^n\right)\to\left(X,\{x_0\}\right)\;\bigg{|}\;\gamma\text{ is continuous }\right\}}{\simeq}$$ where we say that $f\simeq g$ if there exists a homotopy between $f$ and $g$. 
\end{defn}

Notice that the definition coincides with that of the fundamental group when $n=1$, and hence $\pi_n$ is indeed a generalization. 

\begin{lmm}{}{} For any $n\in\N$, the two spaces $(I^n,\partial I^n)$ and $(S^n,s_0)$ are homotopy equivalent. 
\end{lmm}

Therefore an alternate viewpoint of the homotopy groups is instead the collection of maps from the pointed $n$-sphere to the space $X$ quotient homotopy. Indeed an $n$-dimensional sphere has an $n$-dimensional hole enclosed by the sphere itself. Therefore in order to detect $n$-dimensional holes in a space, we are permitted to try and fit $n$-spheres into the space. \\~\\

Spheres are also advantageous for the definition of $\pi_n$ because spheres only has an $n$-dimensional hole and no other holes in any dimension. Therefore we are capturing the minimal amount of information on $n$-dimensional holes without producing excess data. \\~\\

Now we have defined the set $\pi_n(X,x_0)$ for a pointed space to have the word group in its name. We will also need to procure a canonical group structure on the set $\pi_n(X,x_0)$. This will be similar with that of the fundamental group. 

\begin{defn}{Concatenation}{} Let $n\geq 1$. Let $(X,x_0)$ be a pointed space. Let $f,g:(I^n,\partial I^n)\to(X,x_0)$ be maps. Define the composition of $f$ and $g$ by the formula $$(f\cdot g)(t_1,\dots,t_n)=\begin{cases}
f(2t_1,t_2,\dots,t_n) & \text{ if } 0\leq t_1\leq\frac{1}{2}\\
g(2t_1-1,t_2,\dots,t_n) & \text{ if } \frac{1}{2}\leq t\leq 1
\end{cases}$$ for $f,g\in\pi_n(X,x_0)$. 
\end{defn}

Notice that concatenation is really just the same concatenation between elements of the fundamental group but instead with more coordinates. The group structure on $\pi_n(X,x_0)$ uses concatenation and such a proof also uses the same homotopies as in Algebraic Topology 1, but with more coordinates. 

\begin{thm}{}{} Let $(X,x_0)$ be a pointed space and $n\geq 1$. The operation $\cdot$ on the equivalence classes in $\pi_n(X,x_0)$ is well defined and endows it with the structure of a group. \tcbline
\begin{proof}
We first show that the operation is well defined on $\pi_n(X,x_0)$. Suppose that $f_1\overset{\partial}{\simeq} g_1:(I^n,\partial I^n)\to(X,x_0)$ via the homotopy $H_1$ and $f_2\overset{\partial}{\simeq} g_2:(I^n,\partial I^n)\to(X,x_0)$ via the homotopy $H_2$. Consider the map $H:I^n\times[0,1]\to X$ defined by $$H(x_1,\dots,x_n,t)=\begin{cases}
H_1(2x_1,\dots,x_n,t) & \text{if } 0\leq x_1\leq\frac{1}{2}\\
H_2(2x_1-1,\dots,x_n,t) & \text{if }\frac{1}{2}\leq x_1\leq 1
\end{cases}$$ 
Now when $t=0$, we have that $H(x_1,\dots,x_n,0)=f_1\cdot f_2$. When $t=1$, we have that $H(x_1,\dots,x_n,1)=g_1\cdot g_2$. Now notice that by definition of $H_1$ and $H_2$, if one of $x_1,\dots,x_n$ is equal to $0$ or $1$, then $H_1$ and $H_2$ is constant and maps to $x_0$. This means that $H$ also has such property and hence $H$ is a homotopy $(I,\partial I^n)$ to $(X,x_0)$. \\~\\

We now have an appropriate binary operation on $\pi_n(X,x_0)$. It is clearly associative since the composition of maps are associativity and one can re-parametrize homotopies with different traversal speeds. I claim that the constant map $e_{x_0}:(I,\partial I^n)\to(X,x_0)$ defined by $e_{x_0}(x)=x_0$ is the identity. Let $f:(I^n,\partial I^n)\to(X,x_0)$ be arbitrary. Define the homotopy from $e_{x_0}\cdot f$ to $f$ by $$H(x_1,\dots,x_n,t)=\begin{cases}
e_{x_0}(x_1,\dots,x_n)=x_0 & \text{ if }0\leq x_1\leq\frac{1-t}{2}\\
f\left(\frac{2s+t-1}{t+1}\right) & \text{ if }\frac{1-t}{2}\leq x_1\leq 1
\end{cases}$$ A similar homotopy proves that $f\cdot e_{x_0}\simeq f$. For the inverse, I claim that $\overline{f}:(I^n,\partial I^n)\to(X,x_0)$ defined by $\overline{f}(1-x_1,\dots,x_n)$ is the inverse of $f$. Indeed, define a homotopy from $f\cdot\overline{f}$ to $e_{x_0}$ by $$H(x_1,\dots,x_n,t)=\begin{cases}
e_{x_0}(x_1,\dots,x_n)=x_0 & \text{ if }0\leq x_1\leq\frac{t}{2}\text{ or }\frac{1-t}{2}\leq x_1\leq 1\\
f(2x_1-t,x_2,\dots,x_n) & \text{ if }\frac{t}{2}\leq x_1\leq\frac{1}{2}\\
\overline{f}(2s+t-1) & \text{ if }\frac{1}{2}\leq x_1\leq\frac{1-t}{2}
\end{cases}$$
\end{proof}
\end{thm}

However, what makes each $\pi_n(X,x_0)$ for $n\geq 2$ different from the fundamental group $\pi_1(X,x_0)$ is the abelian group structure on $\pi_n(X,x_0)$. 

\begin{thm}{}{} Let $(X,x_0)$ be a pointed space. Then the $n$th homotopy group $$\pi_n(X,x_0)$$ together with concatenation is abelian. \tcbline
\begin{proof}
Define a new operation $\star:\pi_n(X,x_0)\times\pi_n(X,x_0)\to\pi_n(X,x_0)$ by $$[f]\star[g]=\begin{cases}
f(t_1,2t_2,\dots,t_n) & \text{ if } 0\leq t_1\leq\frac{1}{2}\\
g(t_1,2t_2-1,\dots,t_n) & \text{ if } \frac{1}{2}\leq t\leq 1
\end{cases}$$ Such an operation clearly also defines an abelian group structure on $\pi_n(X,x_0)$ using the same argument. Now I want to prove that $$([f]\ast[g])\star([h]\ast [k])=([f]\star [h])\ast([g]\star [k])$$ This is true because $$([f]\ast[g])\star([h]\ast [k])=\begin{cases}
f(2x_1,2x_2,x_3,\dots,x_n) & \text{ if } 0\leq x_1,x_2\leq\frac{1}{2}\\
g(2x_1,2x_2-1,x_3,\dots,x_n) & \text{ if } 0\leq x_1\leq\frac{1}{2} \text{ and } \frac{1}{2}\leq x_2\leq 1\\
h(2x_1-1,2x_2,x_3,\dots,x_n) & \text{ if } \frac{1}{2}\leq x_1\leq 1 \text{ and } 0\leq x_2\leq\frac{1}{2}\\
k(2x_1,2x_2-1,x_3,\dots,x_n) & \text{ if } \frac{1}{2}\leq x_1,x_2\leq 1
\end{cases}$$ and $$([f]\star [h])\ast([g]\star [k])=\begin{cases}
f(2x_1,2x_2,x_3,\dots,x_n) & \text{ if } 0\leq x_1,x_2\leq\frac{1}{2}\\
h(2x_1-1,2x_2,x_3,\dots,x_n) & \text{ if } \frac{1}{2}\leq x_1\leq 1 \text{ and } 0\leq x_2\leq\frac{1}{2}\\
g(2x_1,2x_2-1,x_3,\dots,x_n) & \text{ if } 0\leq x_1\leq\frac{1}{2} \text{ and } \frac{1}{2}\leq x_2\leq 1\\
k(2x_1,2x_2-1,x_3,\dots,x_n) & \text{ if } \frac{1}{2}\leq x_1,x_2\leq 1
\end{cases}$$ which are entirely the same. Now I claim that $\ast=\star$. It is clear that both binary operations have the same identity element $e_{x_0}$. Now we have that $$f\ast g=(f\star 1)\ast (1\star g)=(f\ast 1)\star(1\ast g)=f\star g$$ Finally, I claim that $\ast$ is commutative. We have that $$f\ast g=(1\star f)\ast(g\star 1)=(1\ast g)\star(f\ast 1)=g\star f=g\ast f$$ Thus we conclude. 
\end{proof}
\end{thm}

The above technique is actually called the Eckmann-Hilton argument. In particular, it shows that concatenation of paths need not be defined via the first coordinate. Any choice of coordinate to perform concatenation will result in the same group structure. \\~\\

Geometrically speaking, 

\subsection{Properties of Homotopy}
The homotopy groups also satisfy functorial properties similar to the fundamental group and the (co)homology groups. 

\begin{thm}{Functoriality}{} Let $(X,x_0)$ and $(Y,y_0)$ be pointed spaces and let $f:(X,x_0)\to(Y,y_0)$ be a pointed map. Then the induced map $$\pi_n(f):\pi_n(X,x_0)\to\pi_n(Y,y_0)$$ defined by $[\gamma]\mapsto[f\circ\gamma]$ is a group homomorphism. Moreover, it satisfies the following functorial properties. 
\begin{itemize}
\item If $g:(Y,y_0)\to(Z,z_0)$ is a pointed map then $$\pi_n(g\circ f)=\pi_n(g)\circ\pi_n(f)$$
\item If $\text{id}_{(X,x_0)}:(X,x_0)\to(X,x_0)$ is the identity map then $$\pi_n(\text{id}_{(X,x_0)})=\text{id}_{\pi_n(X,x_0)}$$
\end{itemize} \tcbline
\begin{proof}
Firstly, let us show that it is a group homomorphism. Let $\gamma_1,\gamma_2\in\pi_n(X,x_0)$. We have that $$\pi_n(f)([\gamma_1]\cdot[\gamma_2])=[f\circ(\gamma_1\cdot\gamma_2)]=[f\circ\gamma_1\cdot f\circ\gamma_2]=\pi_n(f)([\gamma_1])\cdot\pi_n(f)([\gamma_2])$$ where the second equality is true because homotopies are preserved under function composition. It remains to show associativity and unitality. 
\begin{itemize}
\item Associativity: We have that $$\pi_n(g\circ f)([\gamma])=[g\circ f\circ\gamma]=\pi_n(g)([f\circ\gamma])=(\pi_n(g)\circ\pi_n(f))([\gamma])$$
\item Unitality: We have that $$\pi_n(\text{id}_{(X,x_0)})([\gamma])=[\text{id}_{(X,x_0)}\circ\gamma]=[\gamma]=\text{id}_{\pi_n(X,x_0)}([\gamma])$$
\end{itemize}
And so we conclude. 
\end{proof}
\end{thm}

Similar to all other functorial properties we have seen throughout algebraic topology, a homeomorphism of spaces give an isomorphism on homotopy groups. Now that we know about category theory, we see that such a result does not depend on the definition of the homotopy groups or the (co)homology groups, but is in fact due to the functorial properties of each invariant. \\~\\

Similar to (co)homology and the fundamental group, the homotopy groups are defined via a quotient with homotopy. Therefore we expect the homotopy groups to not be able to distinguish between homotopy equivalent spaces but not homeomorphic spaces. 

\begin{thm}{Homotopy Equivalence}{} Let $(X,x_0),(Y,y_0)$ be pointed spaces and $f,g:(X,x_0)\to (Y,y_0)$ be pointed maps. If $f$ and $g$ are homotopic, then the induced maps $$\pi_n(f)=\pi_n(g):\pi_n(X,x_0)\to\pi_n(Y,y_0)$$ are equal. Moreover, if $f$ is a homotopy equivalence, then $\pi_n(f)$ is an isomorphism. \tcbline
\begin{proof}
Let $[\gamma]\in\pi_n(X,x_0)$. Suppose that $f$ and $g$ are homotopic via $F:X\times I\to Y$. now define $$H(x_1,\dots,x_n,t)=F(\gamma(x_1,\dots,x_n),t)$$ Then it is clear that $H(x_1,\dots,x_n,0)=f\circ\gamma$ and $H(x_1,\dots,x_n,1)=g\circ\gamma$. Thus $[f\circ\gamma]=[g\circ\gamma]$ and so we conclude that $\pi_n(f)([\gamma])=\pi_n(g)([\gamma])$. \\~\\

If $f$ is a homotopy equivalence, then there exists $g:(Y,y_0)\to(X,x_0)$ such that $g\circ f\simeq\text{id}_{(X,x_0)}$ and $f\circ g\simeq\text{id}_{(Y,y_0)}$. By funtoriality and homotopy equivalence, we have that $$\pi_n(g)\circ\pi_n(f)=\text{id}_{\pi_n(X,x_0)}\;\;\;\;\text{ and }\;\;\;\;\pi_n(f)\circ\pi_n(g)=\text{id}_{\pi_n(Y,y_0)}$$ and so we conclude. 
\end{proof}
\end{thm}

While the theory of covering spaces provided great insight for the structure of the fundamental group as well the space itself, the theory no longer works for higher homotopy groups due to the following proposition. 

\begin{prp}{}{} Let $(X,x_0)$ be a pointed space and let $p:(\tilde{X},\tilde{x}_0)\to(X,x_0)$ be a covering space. Then $p$ induces isomorphisms $$\pi_n(p):\pi_n(\tilde{X},\tilde{x}_0)\overset{\cong}{\longrightarrow}\pi_n(X,x_0)$$ for all $n\geq 2$. 
\end{prp}

While covering spaces no longer prove to be useful for insights on the homotopy groups, fibrations will be the correct analogue of covering spaces to computing the higher homotopy groups. In fact, covering spaces themselves are also fibrations. We will see fibrations in later sections. \\~\\

Similar to the fundamental group, changing the base point via a path induces isomorphisms on homotopy groups with the same space but different base point. 

\begin{thm}{}{} Let $(X,x_0)$ and $(X,x_1)$ be pointed spaces with the same base space. Let $u:I\to X$ be a path from $x_0$ to $x_1$. Define the induced map $$u_\#:\pi_n(X,x_0)\to\pi_n(X,x_1)$$ as follows. For $[\gamma]\in\pi_n(X,x_0)$ define $u_\#([\gamma])$ by first shrinking the domain of $\gamma$ to a smaller concentric cube in $I^n$. Then inserting the path $\gamma$ on each radical segment of the shell between the smaller cube and $\partial I^n$. \\~\\
The construction of $u_\#$ is a group isomorphism. Moreover, it satisfies the following universal properties. 
\begin{itemize}
\item If $v:I\to X$ is a path from $x_1$ to $x_2$ and $u\cdot v$ is the concatenation of these paths, then $$(u\cdot v)_\#=u_\#\circ v_\#$$
\item If $c_{x_0}$ is the constant path from $x_0$ to $x_0$ then $(c_{x_0})_\#$ is the identity
\end{itemize}
\end{thm}

\begin{prp}{}{} Let $(X,x_0)$ and $(X,x_1)$ be pointed spaces with the same base space. Let $u,v:I\to X$ be paths from $x_0$ to $x_1$. If $u$ and $v$ are homotopic relative to end points then the induced maps $$u_\#=v_\#:\pi_n(X,x_0)\to\pi_n(X,x_1)$$ are equal. 
\end{prp}

This shows that if $X$ is path connected, then $\pi_n(X,x_0)$ no longer depends on the choice of base point. Although there are no canonical isomorphisms between $\pi_n(X,x_0)$ and $\pi_n(X,x_1)$, we still forget about the base point in this case and write the homotopy groups as $\pi_n(X)$. 

\begin{prp}{}{} Let $(X,x_0)$ be a pointed space and $f\in\pi_n(X,x_0)$. Let $u:I\to X$ be a loop on $x_0$. Then $u$ induces a left action of $\pi_1(X,x_0)$ on $\pi_n(X,x_0)$ by the map $$(u,\gamma)\mapsto u_\#(\gamma)$$ In particular, for $n\geq 2$, $\pi_n(X,x_0)$ is a $\Z\pi_1(X,x_0)$-module. 
\end{prp}

\begin{prp}{}{} Let $X_i$ for $i\in I$ be a family of path connected spaces. Then there are isomorphisms $$\pi_n\left(\prod_{i\in I}X_i\right)\cong\prod_{i\in I}\pi_n(X_i)$$
\end{prp}

\subsection{Relative Homotopy Groups}
\begin{defn}{Triplets of Spaces}{} Let $X$ be a topological space. A pointed pair of space is a triple $(X,A_1,A_2)$ where $A_2\subseteq A_1\subseteq X$ are subspaces of $X$. A map between triplets of spaces $f:(X,A_1,A_2)\to(Y,B_1,B_2)$ is a map $f:X\to Y$ such that $f(A_1)\subseteq B_1$ and $f(A_2)\subseteq B_2$. \\~\\
If $A_2=\{x_0\}$ is a single point we say that $(X,A,x_0)$ is a pointed pair of spaces. 
\end{defn}

\begin{defn}{Homotopy between Maps of Triplets}{} Let $f,g:(X,A_1,A_2)\to(Y,B_1,B_2)$ be maps triplets of spaces. A homotopy between $f$ and $g$ is a homotopy between $f:X\to Y$ and $g:X\to Y$, namely $H:X\times[0,1]\to Y$ such that $H(A_1\times[0,1])\subseteq B_1$ and $H(A_2\times[0,1])\subseteq B_2$. 
\end{defn}

\begin{defn}{The nth Relative Homotopy Groups}{} Let $(X,A,x_0)$ be a pointed pair of space. Let $n\geq 2$. Regard $I^{n-1}$ sitting inside $I^n$ by $I^{n-1}=\{(x_1,\dots,x_n)\in I^n\;|\;x_n=0\}$ and let $J^{n-1}=\overline{\partial I^n\setminus I^{n-1}}$. Define the relative homotopy groups of the triple by $$\pi_n(X,A,x_0)=\frac{\left\{\gamma:\left(I^n,\partial I^n,J^{n-1}\right)\to\left(X,A,x_0\right)\;\bigg{|}\;\gamma\text{ is continuous }\right\}}{\simeq}$$ where we say that $f\simeq g$ if there exists a homotopy between $f$ and $g$. 
\end{defn}

It is easy to see that $\pi_n(X,x_0,x_0)=\pi_n(X,x_0)$ so that homotopy groups are a special case of the relative homotopy groups. 

\begin{lmm}{}{} For any $n\in\N$, the two triplets $(I^n,\partial I^n,J^{n-1})$ and $(D^n,S^{n-1},s_0)$ are homotopy equivalent. 
\end{lmm}

\begin{thm}{}{} Let $(X,A,x_0)$ be a pointed pair of space. The composition law on definition 1.1.4 defines a group structure on $\pi_n(X,A,x_0)$ for $n\geq 2$. Moreover, $\pi_n(X,A,x_0)$ is abelian for $n\geq 3$. 
\end{thm}

\subsection{Induced Maps of Relative Homotopy Groups}
\begin{thm}{}{} Let $(X,A,x_0)$ and $(Y,B,y_0)$ be pointed pairs of spaces and $f:(X,A,x_0)\to(Y,B,y_0)$ a map. Then $f$ induces a map on the relative homotopy groups $$f_\ast:\pi_n(X,A,x_0)\to\pi_n(Y,B,y_0)$$ for $n\geq 2$ satisfying the following functorial properties: 
\begin{itemize}
\item $f_\ast$ is a group homomorphism
\item If $g:(Y,B,y_0)\to(Z,C,z_0)$ is a map, then $$(g\circ f)_\ast=g_\ast\circ f_\ast$$
\item If $\text{id}_{(X,A,x_0)}$ is the identity map on $(X,A,x_0)$, then $$(\text{id}_{(X,A,x_0)})_\ast=\text{id}_{\pi_n(X,A,x_0)}$$
\end{itemize}
\end{thm}

\begin{thm}{}{} Let $(X,A,x_0),(Y,B,y_0)$ be pointed pairs of spaces and $f,g:(X,A,x_0)\to (Y,B,y_0)$ be pointed maps. If $f$ and $g$ are homotopic, then the induced maps $$f_\ast=g_\ast:\pi_n(X,A,x_0)\to\pi_n(Y,B,y_0)$$ are equal. Moreover, if $f$ is a homotopy equivalence, then $f_\ast$ is an isomorphism. 
\end{thm}

TBA: change of base point isomorphisms. 

\begin{thm}{The Hurewicz Homomorphism}{} Let $(X,A,x_0)$ be a pointed pair of space. Let $u_n$ be a generator of $H_n(S^n)\cong\Z$. Then the map $$h:\pi_n(X,A,x_0)\to H_n(X,A)$$ defined by $[f]\mapsto f_\ast(u_n)$ is a group homomorphism. 
\end{thm}

\subsection{Long Exact Sequence in Homotopy Groups}
\begin{lmm}{Compression Criterion}{} Let $(X,A,x_0)$ be a pair of spaces with basepoint. Let $f:(D^n,S^{n-1},\ast)\to(X,A,x_0)$ be a map. Then $[f]=[e_{x_0}]\in\pi_n(X,A,x_0)$ if and only if $$(f:D^n\to X)\overset{S^{n-1}}{\simeq}(g:D^n\to X)$$ where $g$ is any map such that $g(X)\subseteq A$. \tcbline
\begin{proof}
Suppose that the second criterion is satisfied. Then it clearly shows that $[f]=[g]\in\pi_n(X,A,x_0)$. Let $r:D^n\times I\to D^n$ be a deformation retract from $D^n$ to $\ast\in S^{n-1}\subset D^n$. Consider the map $g\circ r:D^n\times I\to X$. When $t=0$, this is the map $g$. When $t=1$, $g\circ r$ factors through $\ast$ and so becomes a map $\ast\to X$. In other words, it is the constant map $e_{x_0}$. Moreover, it $g\circ r$ has image in $A$ and so in particular it sends $S^{n-1}$ to $A$. Thus $g\circ r$ is a homotopy between $\text{e}_{x_0}$ and $g$. We conclude that $[f]=[g]=[e_{x_0}]$. \\~\\

Now suppose that $[f]=[e_{x_0}]\in\pi_n(X,A,x_0)$ is given by the homotopy $H:D^n\times I\to X$. This means that $H(D^n\times\{1\})\subseteq\{x_0\}\subset A$ and $H(S^{n-1}\times I)\subset A$. Now $D^n\times I$ deformation retracts to the cup $D^n\times\{1\}\cup S^{n-1}\times I$ by radical projection from the center point of $D^n\times\{0\}$. Thus $H$ can be converted into a map from $D^n\times\{1\}\cup S^{n-1}\times I$ to $X$. Then $H$ is now a homotopy from $f$ to a map $H(-,1):D^n\to X$ which has image in $A$, relative to $S^{n-1}$. Thus we conclude. 
\end{proof}
\end{lmm}

\begin{thm}{}{} Let $X$ be a space and $A,B$ be subspaces of $X$ such that $B\subseteq A\subseteq X$. Let $x_0\in B$. Then there is a long exact sequence in relative homotopy groups: \\~\\
\adjustbox{scale=0.88,center}{\begin{tikzcd}
	\cdots & {\pi_n(A,B,x_0)} & {\pi_n(X,B,x_0)} & {\pi_n(X,A,x_0)} & {\pi_{n-1}(A,B,x_0)} & \cdots & {\pi_1(X,A,x_0)}
	\arrow[from=1-1, to=1-2]
	\arrow["{i_\ast}", from=1-2, to=1-3]
	\arrow["{j_\ast}", from=1-3, to=1-4]
	\arrow["{\partial_n}", from=1-4, to=1-5]
	\arrow[from=1-5, to=1-6]
	\arrow[from=1-6, to=1-7]
\end{tikzcd}}\\~\\
where $i:(A,B,x_0)\to(X,B,x_0)$ and $j:(X,B,x_0)\to(X,A,x_0)$ are the inclusions and $\partial:\pi_n(X,A,x_0)\to\pi_{n-1}(A,B,x_0)$ is given by $[\gamma]\mapsto[\gamma|_{I^{n-1}}]$ \tcbline
\begin{proof}{}{}
\end{proof}
\end{thm}

TBA: Naturality of the sequence. 

\begin{thm}{}{} Let $(X,A,x_0)$ be a pointed pair of spaces. The relative homotopy groups and (absolute) homotopy groups of $(X,A,x_0)$ fit into a long exact sequence \\~\\
\adjustbox{scale=0.75,center}{\begin{tikzcd}
	\cdots & {\pi_{n+1}(X,A,x_0)} & {\pi_n(A,x_0)} & {\pi_n(X,x_0)} & {\pi_n(X,A,x_0)} & {\pi_{n-1}(A,x_0)} & \cdots & {\pi_0(X,x_0)} & 0
	\arrow[from=1-1, to=1-2]
	\arrow["{\partial_{n+1}}", from=1-2, to=1-3]
	\arrow["{i_\ast}", from=1-3, to=1-4]
	\arrow["{j_\ast}", from=1-4, to=1-5]
	\arrow["{\partial_n}", from=1-5, to=1-6]
	\arrow[from=1-6, to=1-7]
	\arrow[from=1-8, to=1-9]
	\arrow[from=1-7, to=1-8]
\end{tikzcd}}\\~\\
where $\partial_n$ is defined by $[f]\mapsto [f|_{I^{n-1}}]$ and $i_\ast$ and $j_\ast$ are induced by inclusions. 
\end{thm}

Note that even though at the end of the sequence group structures are not defined, exactness still makes sense: kernels in this case consists of elements that map to the homotopy class of the constant map. 


\subsection{n-Connectedness}
\begin{defn}{n-Connected Space}{} Let $X$ be a space. We say that it is $n$-connected if $$\pi_k(X,x_0)=0$$ for $0\leq k\leq n$ and some $x_0\in X$. 
\end{defn}

Note that $\pi_0(X,x_0)$ implies that $X$ is path connected. Hence the notion of $n$-connectedness does not depend on the base point by the change of base point isomorphism. In particular, $\pi_k(X,x_0)=0$ for $0\leq k\leq n$ and some $x_0\in X$ if and only if $\pi_k(X,x_0)=0$ for $0\leq k\leq n$ for all $x_0\in X$. (Hatcher)

\begin{defn}{n-Connected Pair of Spaces}{} Let $(X,A)$ be a pair of space. We say that it is $n$-connected if $$\pi_k(X,A,x_0)=0$$ for $0\leq k\leq n$ and all $x_0\in A$. 
\end{defn}

TBA: conditions in P.346 of Hatcher

\begin{defn}{Weakly Contractible}{} Let $X$ be a space. We say that $X$ is weakly contractible if $$\pi_n(X)=0$$ for all $n\geq 0$. 
\end{defn}

\pagebreak
\section{Weak Equivalences and CW-Complexes}
\subsection{Weak Homotopy Equivalence}
\begin{defn}{Weak Homotopy Equivalence}{} We say that a map $f:X\to Y$ is a weak homotopy equivalence if it induces isomorphisms on all homotopy groups $\pi_n$ on any choice of base point. 
\end{defn}

TBA: compression lemma in Hatcher

\begin{thm}{}{} Let $X,Y$ be spaces and let $f:X\to Y$ be a weak homotopy equivalence. Then $f$ induces isomorphisms $$f_\ast:H_n(X;G)\overset{\cong}{\longrightarrow}H_n(Y;G)\;\;\;\;\text{ and }\;\;\;\;f^\ast:H^n(Y;G)\overset{\cong}{\longrightarrow}H^n(X;G)$$ for any group $G$ and all $n\in\N$. 
\end{thm}

This theorem shows that the higher homotopy groups is not a weaker invariant than homology and cohomology. Indeed, the theorem states that if the all homotopy groups are isomorphic, then all their (co)homology groups will be isomorphic. 

\begin{prp}{}{} Let $X,Y$ be spaces and let $f:X\to Y$ be a weak homotopy equivalence. Then $f$ induces bijections $$[Z,X]\cong[Z,Y]\;\;\;\;\text{ and }\;\;\;\;[Z,X]_\ast\cong[Z,Y]_\ast$$ for all CW-complexes $Z$. 
\end{prp}

\subsection{Whitehead's Theorem}
\begin{thm}{Whitehead's Theorem}{} If $X$ and $Y$ are CW-complexes and $f:X\to Y$ is a weak homotopy equivalence, then $f$ is a homotopy equivalence. 
\end{thm}

TBA: extension lemma in Hatcher. 

\begin{crl}{}{} If $X$ and $Y$ are CW-complexes with $\pi_1(X)=\pi_1(Y)=0$ and $f:X\to Y$ induces isomorphisms on homology groups $H_n$ for all $n$, then $f$ is a homotopy equivalence. 
\end{crl}

\subsection{Cellular Approximations}
\begin{defn}{Cellular Maps}{} Let $X$ and $Y$ be CW-complexes. A map $f:X\to Y$ is called cellular if $f(X_n)\subset Y_n$ for all $n$, where $X_n$ is the $n$-skeleton of $X$. 
\end{defn}

\begin{defn}{Cellular Approximations}{} Let $X$ and $Y$ be CW-complexes. We say that $f:X\to Y$ has a cellular approximations if $f$ is homotopic to a cellular map $f':X\to Y$. 
\end{defn}

\begin{thm}{Cellular Approximation Theorem}{} Any map $f:X\to Y$ between CW-complexes has a cellular approximation $f':X\to Y$. Moreover, if $f$ is already cellular on a subcomplex $A\subseteq X$, then we can take $f'|_A=f|_A$. 
\end{thm}

\begin{thm}{Relative Cellular Approximation}{} Any map $f:(X,A)\to (Y,B)$ between pairs of CW-complexes has a cellular approximation. 
\end{thm}

\begin{crl}{}{} Let $A\subset X$ be CW-complexes and suppose that all cells $X\setminus A$ have dimension larger than $n$. Then $(X,A)$ is $n$-connected. 
\end{crl}

\begin{crl}{}{} Let $X$ be a CW complex and let $X^n$ be its $n$-skeleton. Then $(X,X^n)$ is $n$-connected. Moreover, the inclusion $X^n\hookrightarrow X$ induces an isomorphism $$\pi_k(X^n)\to\pi_k(X)$$ for $0\leq k<n$ and a surjection for $k=n$. 
\end{crl}

\subsection{CW Approximations}
\begin{defn}{CW Approximation}{} Let $X$ be a space. A CW approximation of $X$ is a weak homotopy equivalence $f:Z\to X$ where $Z$ is a CW complex. 
\end{defn}

The goal of this section is that every space has a CW approximation. The given homotopy equivalence makes this notion powerful because this means that for any space $X$, there exists a CW-complex such that $X$ and $Z$ are homotopy equivalent, and moreover, has isomorphic homotopy, homology and cohomology groups. 

\begin{defn}{CW Model}{} Let $(X,A)$ be a non-empty pair of CW-complexes. An $n$-connected CW model of $(X,A)$ is an $n$-connected CW pair $(Z,A)$ together with a map $f:Z\to X$ with $f|_A=\text{id}_A$ such that $$f_\ast:\pi_i(Z)\to\pi_i(X)$$ is an isomorphism for $i>n$ and an injection for $i=n$ for any choice of base point. 
\end{defn}

\begin{thm}{}{} For any non-empty pair $(X,A)$ of CW-complexes, there exists an $n$-connected model $(Z,A)$. Moreover, $Z$ can be built from $A$ by attaching cells of dimension greater than $n$. 
\end{thm}

\begin{thm}{}{} Every pair of spaces $(X,A)$ has a CW approximation. Such a CW approximation is unique up to homotopy equivalence. 
\end{thm}

\pagebreak

\section{Main Results of Homotopy Theory on CW-Complexes}
\subsection{Excision for Homotopy Groups}
\begin{thm}{The Homotopy Excision Theorem}{} Let $X$ be a CW-complex and $A,B$ be sub complexes such that $X=A\cup B$ and $A\cap B\neq\emptyset$. If $(A,A\cap B)$ is $m$-connected and $(B,A\cap B)$ is $n$-connected for $m,n\geq 0$, then the map $$\iota_\ast:\pi_i(A,A\cap B)\to(X,B)$$ induced by the inclusion $\iota:(A,A\cap B)\to(X,B)$ is an isomorphism for $0\leq i<m+n$ and a surjection for $i=m+n$. 
\end{thm}

\begin{prp}{}{} Let $(X,A)$ be a pair of $r$-connected CW complexes and let $A$ be $s$-connected. Then the map $$p_\ast:\pi_k(X,A)\to\pi_k(X/A)$$ induced by the quotient map $p:X\to X/A$ is an isomorphism for $0\leq k\leq r+s$ and a surjection for $k=r+s+1$. 
\end{prp}

\subsection{Freudenthal Suspension Theorem}
\begin{defn}{Reduced Suspension}{} Let $(X,x_0)$ be a pointed space. Define the reduced suspension of $X$ to be the space $$\Sigma X=\frac{X\times I}{(X\times\{0\}\cup X\times\{1\}\cup\{x_0\}\times I)}$$
\end{defn}

The reduced suspension defines a continuous map sending a space $X$ to its reduced suspension $\Sigma X$. 

\begin{thm}{Freudenthal Suspension Theorem}{} Let $X$ be an $n$-connected CW complex. Then for $0\leq k\leq 2n$, the induced map $$\Sigma_\ast:\pi_k(X)\to\pi_{k+1}(\Sigma X)$$ is an isomorphism. For $k=2n+1$, $\Sigma_\ast$ is a surjection. 
\end{thm}

We can keep on suspending the space and the maps. Indeed if $X$ is $n$-connected then, by Freudenthal suspension theorem $\Sigma X$ is $(n+1)$-connected. We can then apply the suspension theorem again on $\Sigma X$ and we see that $\Sigma^2X$ is $(n+2)$-connected. 

\begin{crl}{}{} There is an isomorphism $$\pi_{n+k}(S^n)\cong\pi_{n+k+1}(S^{n+1})$$ for all $n\geq k+2$. 
\end{crl}

\begin{prp}{}{} Let $X$ be a space. Let $k\in\N$. Then the the following sequence of suspensions $$\pi_k(X)\to\pi_{k+1}(\Sigma X)\to\pi_{k+2}(\Sigma^2X)\to\cdots$$ are eventually isomorphisms. \tcbline
\begin{proof}
Let $X$ be $n$-connected. There are two cases. \\~\\

Let $k\leq 2n$. By Freudenthal suspension theorem, if $k\leq 2n$ then $\pi_k(X)\cong\pi_{k+1}(\Sigma X)$. Then $\Sigma X$ is $(n+1)$-connected hence $\pi_{k+1}(\Sigma X)\cong\pi_{k+2}(\Sigma^2X)$ is an isomorphism since $k+1\leq 2n+2$. More generally, for $r\in\N$, $\Sigma^rX$ is $(r+n)$-connected hence $$\pi_{k+r}(\Sigma^rX)\cong\pi_{k+r+1}(\Sigma^{r+1}X)$$ is an isomorphism since $k+r\leq 2n+2r$. \\~\\

Now if $k>2n$, then there exists $r\in\N$ such that $k+r\leq 2n+2r$. Such an $r$ is given by say $k-2n$. Then by Freudenthal suspension theorem, $$\pi_{k+r}(\Sigma^rX)\cong\pi_{k+r+1}(\Sigma^{r+1}X)$$ is an isomorphism. More generally, for $m\in\N$, $\Sigma^{r+m}X$ is $(r+m+n)$-connected hence $$\pi_{k+r+m}(\Sigma^{r+m}X)\cong\pi_{k+r+m+1}(\Sigma^{r+m+1}X)$$ is an isomorphism since $k+r+m\leq 2n+2r+2m$. 
\end{proof}
\end{prp}

\begin{defn}{Stable Homotopy Groups}{} Let $X$ be a space. Let $n\in\N$. Define the $n$th stable homotopy groups of $X$ to be $$\pi_n^s(X)=\colim_{k\to\infty}\pi_{n+k}(\Sigma^kX)$$
\end{defn}

\subsection{Hurewicz's Theorem}
\begin{thm}{Hurewicz's Homomorphism}{} Let $X$ be a path connected space. Then for any $n\in\N$, there is a group homomorphism $$h_n:\pi_n(X)\to H_n(X)$$ called the Hurewicz homomorphism, defined as follows. Let $[u_n]\in H_n(S^n)$ be a canonical generator. Then $h_n([f])=f_\ast(u_n)$. 
\end{thm}

\begin{thm}{Hurewicz's Theorem}{} Let $X$ be a space. Then the following are true regarding Hurewicz's homomorphism. 
\begin{itemize}
\item Let $n\geq 2$. If $X$ is $(n-1)$-connected, then $\widetilde{H}_k(X)=0$ for all $0\leq k<n$. Moreover, the Hurewicz homomorphism $$h_n:\pi_n(X)\to H_n(X)$$ is an isomorphism. Moreover, $h_{n+1}$ is a surjection. 
\item Let $n=1$, then Hurewicz's homomorphism induces an isomorphism $$\overline{h_1}:\pi_1(X)^\text{ab}\to H_1(X)$$ 
\end{itemize}
\end{thm}

\begin{thm}{Relative Hurewicz's Homomorphism}{} Let $(X,A)$ be a pair of spaces. Then for any $n\geq 1$, there is a group homomorphism $$h_n:\pi_n(X,A)\to H_n(X,A)$$ called the relative Hurewicz homomorphism, defined as follows. Let $[u_n]\in H_n(S^n,\partial S^n)$ be a canonical generator. Then $h_n([f])=f_\ast(u_n)$. 
\end{thm}

\begin{thm}{Relative Hurewicz's Theorem}{} Let $(X,A)$ be a pair of spaces. Let $n\geq 2$. If $X$ and $A$ are path connected and $(X,A)$ is $(n-1)$-connected, then $H_k(X,A)=0$ for all $0\leq k<n$. Moreover, the Hurewicz homomorphism $$h_n:\pi_n(X,A,x_0)\to H_n(X,A)$$ is an isomorphism. 
\end{thm}

\begin{thm}{Naturality of Hurewicz's Homomorphism}{} Let $(X,x_0)$ and $(Y,y_0)$ be pointed spaces and let $f:(X,x_0)\to(Y,y_0)$ be a map. Then the following diagram is commutative: \\~\\
\adjustbox{scale=1,center}{\begin{tikzcd}
	{\pi_k(X,x_0)} & {\pi_k(Y,y_0)} \\
	{H_k(X)} & {H_k(Y)}
	\arrow["{\pi_k(f)}", from=1-1, to=1-2]
	\arrow["{h_k}"', from=1-1, to=2-1]
	\arrow["{h_k}", from=1-2, to=2-2]
	\arrow["{f_\ast}"', from=2-1, to=2-2]
\end{tikzcd}}\\~\\
where $h$ is the Hurewicz homomorphism. Moreover, a similar diagram is also commutative for the relative Hurewicz homomorphism. 
\end{thm}

The connection between the homotopy groups and the homology groups begs the question of whether there is a relationship between the homotopy groups and cohomology groups that is not implicit by the relation between homology and cohomology. This is answered in Stable Homotopy Theory, when we introduced Brown's representability theorem. 

\subsection{Eilenberg-MacLane Spaces}
\begin{defn}{Eilenberg-MacLane Space}{} Let $G$ be a group and $n\in\N$. We say that a space $X$ is an Eilenberg-MacLane space of type $K(G,n)$ if $$\pi_k(X)=\begin{cases}
K(G,n) & \text{ if } k=n\\
0 & \text{ otherwise }
\end{cases}$$
\end{defn}

We often denote this space $X$ directly by $X=K(G,n)$. 

\begin{prp}{}{} Let $G$ be a group. Then there exists a $K(G,1)$-CW complex. 
\end{prp}

\begin{thm}{}{} Let $G$ be an abelian group and $n\geq 2$. Then there exists a $K(G,n)$-CW complex. Moreover, it is uniquely determined by $G$ and $n$. 
\end{thm}

The Eilenberg-Maclane spaces are a fundamental object of study in algebraic topology because it is a universal object. This is again part of Stable Homotopy Theory and is the same theorem that gives the connection between homotopy groups and cohomology groups. \\~\\

We will not prove this here, but we will give the theorem: If $G$ is an abelian group, then there are natural isomorphisms $$H^n(X;G)\cong[X,K(G,n)]_\ast$$ that is natural in the following sense. If $f:X\to Y$ is a map, then there is a commutative diagram: \\~\\
\adjustbox{scale=1,center}{\begin{tikzcd}
	{H^n(Y;G)} & {H^n(X;G)} \\
	{[Y,K(G,n)]_\ast} & {[X,K(G,n)]_\ast}
	\arrow["{f^\ast}", from=1-1, to=1-2]
	\arrow["\cong"', from=1-1, to=2-1]
	\arrow["\cong", from=1-2, to=2-2]
	\arrow["{f^\ast}"', from=2-1, to=2-2]
\end{tikzcd}}\\~\\

\pagebreak
\section{The Categorical Viewpoint}
Recall that the category of topological spaces $\bold{Top}$ is complete and cocomplete. This means that all kinds of limits and colimits exists in $\bold{Top}$. We have already seen the product space and disjoint union with their universal property as a limit / colimit. There are also more constructs that can be recognized / defined in terms of the universal property. 

\subsection{Different Categories of Spaces}
\begin{defn}{The Category of Pointed Topological Spaces}{} Define the category of pointed topological spaces $\bold{Top}_\ast$ to consist of the following data. 
\begin{itemize}
\item The objects are a pair $(X,x_0)$ where $X$ is a topological space and $x_0\in X$ is a chosen base point. 
\item For $(X,x_0)$ and $(Y,y_0)$ two pointed spaces, the morphisms $$\Hom_{\bold{Top}_\ast}((X,x_0),(Y,y_0))=\{f:X\to Y\;|\;f\text{ is continuous and }f(x_0)=y_0\}$$ are the continuous maps from $X$ to $Y$ such that base points are preserved. 
\item Composition is defined as the composition of functions such that base point is preserved. 
\end{itemize}
\end{defn}

\begin{prp}{}{} Let $(X,x_0)$ and $(Y,y_0)$ be pointed spaces. Then the product and coproduct of the two spaces in $\bold{Top}_\ast$ are $$(X\times Y,(x_0,y_0))\;\;\;\;\text{ and }\;\;\;\;(X\vee Y,x_0=y_0)$$ respectively. 
\end{prp}

\begin{defn}{The Category of CW Complexes}{} Define the category of CW complexes $\bold{CW}$ to consist of the following data. 
\begin{itemize}
\item The objects are CW complexes. 
\item For $X$ and $Y$ two CW complexes, the morphisms $$\Hom_{\bold{CW}}(X,Y)=\{f:X\to Y\;|\;f\text{ is continuous}\}$$ are the continuous maps from $X$ to $Y$. 
\item Composition is defined as the composition of functions. 
\end{itemize}
Define similarly the category $\bold{CW}_\ast$ of pointed topological spaces. 
\end{defn}

\begin{defn}{The Category of Pairs of Spaces}{} Define the category of pairs of topological spaces $\bold{Top}^2$ to consist of the following data. 
\begin{itemize}
\item The objects are a pair $(X,A)$ where $X$ is a topological space $A\subseteq X$ is a subspace of $X$. 
\item For $(X,A)$ and $(Y,B)$ two pointed spaces, the morphisms $$\Hom_{\bold{Top}^2}((X,A),(Y,B))=\{f:X\to Y\;|\;f\text{ is continuous and }f(A)\subseteq B\}$$ are the continuous maps from $X$ to $Y$ such that subspaces are mapped to subspaces. 
\item Composition is defined as the composition of functions such that subspaces are mapped to subspaces. 
\end{itemize}
Define similarly the category $\bold{CW}^2$ of pairs of CW complexes. 
\end{defn}

\begin{defn}{Homotopy Category of Spaces}{} Define the homotopy category of topological spaces $\bold{hTop}$ to consist of the following data. 
\begin{itemize}
\item The objects are topological spaces. 
\item For $X$ and $Y$ two spaces, the morphisms $$\Hom_{\bold{CW}}(X,Y)=\{f:X\to Y\;|\;f\text{ is continuous}\}/\sim$$ are the homotopy classes of continuous maps from $X$ to $Y$. 
\item Composition is defined as the composition of functions. 
\end{itemize}
Define similar the homotopy category $\bold{hTop}_\ast$ of pointed topological spaces and pointed homotopy classes of maps. 
\end{defn}

\subsection{Categorical Constructs in the Category of Spaces}
\begin{defn}{Adjunction Spaces}{} Let $X,Y$ be spaces and $A\subseteq X$ a subspace. Let $f:A\to Y$ be a map. Define the adjunction space of $X$ and $Y$ to be  the space $$X\amalg_fY=\frac{X\amalg Y}{a\sim f(a)}$$ together with the quotient topology. 
\end{defn}

\begin{prp}{}{} Let $X,Y$ be spaces and $A\subseteq X$ a subspace of $X$. Let $f:A\to Y$ be a map. Then the adjunction space $X\amalg_f Y$ is a pushout of $f$ and $i:A\to X$ in $\bold{Top}$. 
\end{prp}

\begin{prp}{}{} Let $X,Y$ be spaces with chosen base point $x_0$ and $y_0$ respectively. Then the wedge product $$X\vee Y=X\amalg_fY$$ is an adjunction space with $Z=\{x_0\}$ and map $f:Z\to Y$ defined by $f(x_0)=y_0$. 
\end{prp}

\subsection{Reduced Suspension and Loop Space Adjunction}
\begin{defn}{Loop Spaces}{} Let $X$ be a space with a chosen basepoint. Define the loop space of $(X,x_0)$ to be $$\Omega X=\Hom_\bold{Top}(S^1,X)$$ together with the compact open topology. If $X$ is pointed with $x_0\in X$ then we choose the constant loop $c_{x_0}$ to be the base point of $\Omega X$. 
\end{defn}

\begin{lmm}{}{} Let $G$ be an abelian group and let $n\in\N$. Then there is a homeomorphism $$\Omega K(G,n)\cong K(G,n-1)$$
\end{lmm}

\begin{thm}{}{} The operations $\Sigma$ and $\Omega$ define functors on $\bold{Top}$, $\bold{Top}_\ast$, $\bold{hTop}$ and $\bold{hTop}_\ast$ as follows. 
\begin{itemize}
\item $\Sigma$ and $\Omega$ sends a pointed space $(X,x_0)$ to $$(\Sigma X,(x_0,0))\;\;\;\;\text{ and }\;\;\;\;(\Omega X,c_{x_0})$$ respectively. The non-basepoint version is obtained by forgetting the base point. 
\item For the non homotopy categories, $\Sigma$ and $\Omega$ sends a map $f:X\to Y$ to $$\Sigma f:\Sigma X\to\Sigma Y\;\;\;\;\text{ and }\;\;\;\;\Omega f:\Omega X\to\Omega Y$$ respectively defined by $\Sigma f([x,t])=[f(x),t]$ and $\Omega f(\gamma)=f\circ\gamma$. It is in particular base point preserving. 
\item For the homotopy categories, $\Sigma$ and $\Omega$ sends a homotopy class of maps $[X,Y]$ to $$[\Sigma X,\Sigma Y]\;\;\;\;\text{ and }\;\;\;\;[\Omega X,\Omega Y]$$ respectively given by the same formula as above. It is in particular also base point preserving. 
\end{itemize}
\end{thm}

The following theorem is also said to be the Freudenthal suspension theorem. 

\begin{thm}{}{} Let $Y$ be $(n-1)$-connected. Consider the reduced suspension functor $\Sigma:\bold{hTop}_\ast\to\bold{hTop}_\ast$. Then $\Sigma:[X,Y]\to[\Sigma X,\Sigma Y]$ is bijective if $\dim(X)<2n-1$. Moreover, it is a surjection if $\dim(X)=2n-1$. 
\end{thm}

\begin{thm}{}{} The functor $\Sigma:\bold{hTop}\to\bold{hTop}$ is a left adjoint to the functor $\Omega:\bold{hTop}\to\bold{hTop}$. Explicitly, if $X,Y$ are spaces, there is a bijection of sets $$[\Sigma X,Y]\cong[X,\Omega Y]$$ that is natural in the following sense. If $f:X\to X'$ and $g:Y\to Y'$ are maps, then the following squares are commutative: \\~\\
\adjustbox{scale=1,center}{\begin{tikzcd}
	{[\Sigma X,Y]} & {[X,\Omega Y]} &&& {[\Sigma X,Y]} & {[X,\Omega Y]} \\
	{[\Sigma X',Y]} & {[X',\Omega Y]} &&& {[\Sigma X,Y']} & {[X,\Omega Y']}
	\arrow["\cong", from=1-1, to=1-2]
	\arrow["{(\Sigma f)^\ast}"', from=1-1, to=2-1]
	\arrow["{f^\ast}", from=1-2, to=2-2]
	\arrow["\cong", from=1-5, to=1-6]
	\arrow["{g_\ast}"', from=1-5, to=2-5]
	\arrow["{(\Omega g)_\ast}", from=1-6, to=2-6]
	\arrow["\cong"', from=2-1, to=2-2]
	\arrow["\cong"', from=2-5, to=2-6]
\end{tikzcd}}\\~\\
\end{thm}

\begin{thm}{}{} The functor $\Sigma:\bold{hTop}_\ast\to\bold{hTop}_\ast$ is a left adjoint to the functor $\Omega:\bold{hTop}_\ast\to\bold{hTop}_\ast$. Explicitly, if $X,Y$ are pointed spaces, there is a bijection of sets $$[\Sigma X,Y]_\ast\cong[X,\Omega Y]_\ast$$ that is natural in the following sense. If $f:X\to X'$ and $g:Y\to Y'$ are pointed maps, then the following squares are commutative: \\~\\
\adjustbox{scale=1,center}{\begin{tikzcd}
	{[\Sigma X,Y]_\ast} & {[X,\Omega Y]_\ast} &&& {[\Sigma X,Y]_\ast} & {[X,\Omega Y]_\ast} \\
	{[\Sigma X',Y]_\ast} & {[X',\Omega Y]_\ast} &&& {[\Sigma X,Y']_\ast} & {[X,\Omega Y']_\ast}
	\arrow["\cong", from=1-1, to=1-2]
	\arrow["{(\Sigma f)^\ast}"', from=1-1, to=2-1]
	\arrow["{f^\ast}", from=1-2, to=2-2]
	\arrow["\cong", from=1-5, to=1-6]
	\arrow["{g_\ast}"', from=1-5, to=2-5]
	\arrow["{(\Omega g)_\ast}", from=1-6, to=2-6]
	\arrow["\cong"', from=2-1, to=2-2]
	\arrow["\cong"', from=2-5, to=2-6]
\end{tikzcd}}\\~\\
\end{thm}

Switzer / Hatcher

\begin{defn}{Group Structure on Loop Spaces}{} Let $X$ be a space. Define a group structure on $\Omega X$ as follows. Let $\cdot:\Omega X\times\Omega X\to\Omega X$ be defined as the concatenation: $(f,g)\mapsto f\cdot g$. 
\end{defn}

\begin{prp}{}{} Let $X,Y$ be spaces. Then the group structure on $\Omega Y$ endows $[X,\Omega Y]_\ast$ with a group structure defined as follows. The binary operation $+:[X,\Omega Y]_\ast\times[X,\Omega Y]_\ast\to[X,\Omega Y]_\ast$ is defined by $$([f],[g])\mapsto[f+g]$$ where $f+g:X\to\Omega Y$ is defined by $(f+g)(x)=f(x)\cdot g(x)$. 
\end{prp}

\begin{prp}{}{} Let $X,Y$ be spaces. Then for $n\geq 2$, the group $$[X,\Omega^n Y]_\ast$$ is abelian. 
\end{prp}

By the set bijection $[\Sigma^nX,Y]_\ast\cong[X,\Omega^nY]_\ast$, we can endow the structure of a group on $[\Sigma^nX,Y]_\ast$. 

\pagebreak
\section{The Category of Compactly Generated Spaces}
There is a huge inconvenience when working with $\bold{Top}$ and $\bold{Top}_\ast$ and that is because in general, the mapping space $X^Y$ only exists for $Y$ when $Y$ is imposed with extra condition. Such a space is important for a few reasons. \\~\\

For that reason, it is better to work with a category in which the exponential object $X^Y$ exists and lies inside such a category, while not restricting a wide number of classes of spaces so that the notion of homotopies still make sense and is well defined within such a category. \\~\\

The category of compactly generated spaces has the following advantages: 
\begin{itemize}
\item The smash product $X\wedge Y$ is associative. This means that there are natural isomorphisms $(X\wedge Y)\wedge Z\cong X\wedge(Y\wedge Z)$
\item $X^Y$ now has a canonical topology. 
\item There is an adjunction between the smash product $-\;\wedge\;-$ and the mapping space $\text{Map}_\ast(-,-)$
\end{itemize}

While we have not encountered such notions yet, we also like to add that geometric realization of compact generated spaces preserves products. \\~\\

Due to the huge advantages given to the smash product and mapping spaces, such advantages descend to the two important functors: the suspension and loopspace functors, making such a category an ideal universe for working with fibrations and cofibrations in the next section. 

\subsection{Compactly Generated Spaces}
\begin{defn}{Compactly Generated Spaces}{} Let $X$ be a space. We say that $X$ is compactly generated ($k$-space) if for every set $A\subseteq X$, $A$ is open if and only if $A\cap K$ is open in $K$ for every compact subspace $K\subseteq X$. 
\end{defn}

\begin{defn}{Category of Compactly Generated Spaces}{} Define the category of compactly generated spaces $\bold{CG}$ to be the full subcategory of $\bold{Top}$ consisting of spaces that are compactly generated. In other words, $\bold{CG}$ consists of the following data: 
\begin{itemize}
\item $\text{Obj}(\bold{CG})$ consists of all spaces that are compactly generated. 
\item For $X,Y\in\text{Obj}(\bold{CG})$, the morphisms are $$\Hom_{\bold{CG}}(X,Y)=\Hom_{\bold{Top}}(X,Y)$$
\item Association is given by composition of functions. 
\end{itemize}
Define similarly the category of pointed compactly generated spaces $\bold{CG}_\ast$. 
\end{defn}

\begin{defn}{New $k$-space from Old}{} Let $X$ be a space. Define $k(X)$ to be the set $X$ together with the topology defined as follows: $A\subseteq X$ is open if and only if $A\cap K$ is open in $K$ for every compact subspace $K\subseteq X$. 
\end{defn}

\begin{lmm}{}{} Let $X$ be a space. Then $k(X)$ is a compactly generated space. 
\end{lmm}

Unfortunately $X\times Y$ may not be compactly generated even when $X$ and $Y$ are. But as it turns out, products do exists in $\mathcal{K}$ and are given by $k(X\times Y)$. 

\begin{prp}{}{} Let $X,Y$ be compactly generated spaces. Then the categorical product of $X$ and $Y$ in the category of compactly generated spaces is given by $$k(X\times Y)$$
\end{prp}

\begin{prp}{}{} Every CW complex is compactly generated. 
\end{prp}

\subsection{Adjunctions in CG Spaces}
\begin{defn}{The Mapping Space}{} Let $X$ and $Y$ be compactly generated. Define the mapping space of $X$ and $Y$ by $$\text{Map}(X,Y)=Y^X=k(\Hom_{\mK}(X,Y))$$
\end{defn}

\begin{thm}{}{} Let $X,Y,Z$ be compactly generated. Then the functors $k(-\times Y):\mK\to\mK$ and $\text{Map}(Y,-):\mK\to\mK$ are adjoint functors with the adjunction formula $$\Hom_{\mK}(k(X\times Y),Z)\cong\Hom_{\mK}(X,\text{Map}(Y,Z))$$ Moreover, by giving the Hom set the compact open topology and applying $k$, we obtain an isomorphism $$\text{Map}(k(X\times Y),Z)\cong\text{Map}(X,\text{Map}(Y,Z))$$
\end{thm}

Aside from the adjunction between the product space and the mapping space, another major reason one considers compactly generated spaces is that the smash product gives another adjunction. 

\begin{defn}{The Smash Product}{} Let $(X,x_0)$ and $(Y,y_0)$ be pointed topological spaces. Define the smash product of the two pointed spaces to be the pointed space $$X\wedge Y=\frac{X\times Y}{X\vee Y}$$ together with the point $(x_0,y_0)$. 
\end{defn}

\begin{prp}{}{} Let $X,Y,Z$ be compactly generated spaces with a chosen base point. Then the following are true. 
\begin{itemize}
\item $(X\wedge Y)\wedge Z\cong X\wedge(Y\wedge Z)$
\item $X\wedge Y\cong Y\wedge X$
\end{itemize}
\end{prp}

\begin{thm}{}{} The category $\bold{CG}$ of compactly generated spaces is a symmetric monoidal category with operator the smash product $\wedge:\bold{CG}\times\bold{CG}\to\bold{CG}$ and the unit $S^0$. 
\end{thm}

Note that this is not true if we do not restrict the spaces to the category of compactly generated spaces. 

\begin{lmm}{}{} Let $X$ be a space. Then the reduced suspension and the smash product with the circle $$\Sigma X\cong X\wedge S^1$$ are homeomorphic spaces. 
\end{lmm}

\begin{thm}{}{} Let $X,Y,Z$ be compactly generated with a chosen basepoint. Then the functors $-\wedge Y:\mK_\ast\to\mK_\ast$ and $\text{Map}_\ast(Y,-):\mK_\ast\to\mK_\ast$ are adjoint functors with the adjunction formula $$\Hom_{\mK_\ast}(X\wedge Y,Z)\cong\Hom_{\mK_\ast}(X,\text{Map}_\ast(Y,Z))$$ Moreover, by giving the Hom set the compact open topology and applying $k$, we obtain an isomorphism $$\text{Map}_\ast(X\wedge Y,Z)\cong\text{Map}_\ast(X,\text{Map}_\ast(Y,Z))$$
\end{thm}

\begin{crl}{}{} Let $X$ be a compactly generated space with a chosen basepoint. Then there is a natural homeomorphism $$\text{Map}_\ast(\Sigma X,Y)\cong\text{Map}_\ast(X,k(\Omega Y))$$ given by adjunction of the functors $-\wedge S^1:\mK_\ast\to\mK_\ast$ and $\text{Map}_\ast(S^1,-):\mK_\ast\to\mK_\ast$. 
\end{crl}

\subsection{The Mapping Cylinder and the Mapping Path Space}
Equipped with the Cartesian closed structure in $\bold{CG}$ together with a canonical topology on the mapping space $Y^X$, we can now talk about the duality between the mapping cylinder and the mapping path space. 

\begin{defn}{Mapping Cylinder}{} Let $X,Y$ be spaces and let $f:X\to Y$ a map. Define the mapping cylinder of $f$ to be $$M_f=\frac{(X\times I)\amalg Y}{(x,0)\sim f(x)}=(X\times I)\amalg_fY$$ for $f:X\times\{1\}\cong X\to Y$ together with the quotient topology. 
\end{defn}

\begin{lmm}{}{} Let $X,Y$ be spaces and let $f:X\to Y$ be a map. Then $Y$ is a deformation retract of $M_f$. 
\end{lmm}

The mapping cone, as its name suggests, can be thought of as the mapping cylinder but with one of one of the ends of the cylinder collapsed to a point. 

\begin{defn}{Mapping Cones}{} Let $X,Y$ be spaces and let $f:X\to Y$ be a map. Define the mapping cone of $f$ to be $$C_f=\frac{(X\times I)\amalg Y}{(x,1)\sim f(x),(x,0)\sim(x',0)}$$
\end{defn}

\begin{defn}{The Mapping Path Space}{} Let $X,Y$ be spaces and let $f:X\to Y$ be a map. Define the map $\pi:Y^I\to Y$ by $\pi(\phi)=\phi(0)$. Define the mapping path space to be $$P_f=f^\ast(Y^I)=\{(x,\phi)\subseteq X\times Y^I\;|\;f(x)=\pi(\phi)=\phi(0)\}$$
\end{defn}

The mapping path space satisfy the dual of the universal property of the mapping cylinder. In particular, it is a pullback in $\bold{Top}$. 

\begin{prp}{}{} Let $X,Y$ be spaces and let $f:X\to Y$ be a map. Then the mapping path space $P_f$ is the pullback of $\pi:Y^I\to Y$ and $f$ in $\bold{Top}$. 
\end{prp}

\begin{defn}{Mapping Fiber}{} Let $X,Y$ be spaces and let $f:X\to Y$ be a map. Define the mapping fiber of $f$ to be $$F_f=\{(x,\phi)\in X\times Y^I\;|\;f(x)=\phi(1)\}$$
\end{defn}

The mapping fiber is a natural dual of the mapping cone. 

\pagebreak
\section{Fibrations and Cofibrations}
\subsection{Fibrations and The Homotopy Lifting Property}
\begin{defn}{The Homotopy Lifting Property}{} Let $p:E\to B$ be a map and let $X$ be a space. We say that $p$ has the homotopy lifting property with respect to $X$ if for every homotopy $H:X\times I\to B$ and a lift $\widetilde{H(-,0)}:X\to E$ of $H(-,0)$, there exists a homotopy $\widetilde{H}:X\times I\to E$ such that the following diagram commutes: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{X\times\{0\}} && E \\
	\\
	{X\times I} && B
	\arrow["H"', from=3-1, to=3-3]
	\arrow["{\exists\widetilde{H}}"{description}, dashed, from=3-1, to=1-3]
	\arrow["p", from=1-3, to=3-3]
	\arrow["\iota"', hook, from=1-1, to=3-1]
	\arrow["{\widetilde{H(-,0)}}", from=1-1, to=1-3]
\end{tikzcd}}\\~\\
\end{defn}

\begin{defn}{Fibrations}{} We say that a map $p:E\to B$ is a fibration if it has the homotopy lifting property with respect to all topological spaces $X$. We call $B$ the base space and $E$ the total space. 
\end{defn}

\begin{defn}{Pullbacks of a Fibration}{} Let $p:E\to B$ be a fibration and let $f:B'\to B$ be a continuous map. Define the pullback of $p$ by $f$ to be $$f^\ast(E)=\{(b',e)\in B'\times E\;|\;f(b')=p(e)\}$$ together with the projection map $p_f:f^\ast(E)\to B'$. 
\end{defn}

\begin{prp}{}{} Let $p:E\to B$ be a fibration and let $f:B'\to B$ be continuous. Then the map $f^\ast(E)\to B'$ is a fibration. Moreover, the following diagram commutes: \\~\\
\adjustbox{scale=1,center}{\begin{tikzcd}
	{f^\ast(E)} & E \\
	{B'} & B
	\arrow[from=1-1, to=1-2]
	\arrow["{p_f}"', from=1-1, to=2-1]
	\arrow["p", from=1-2, to=2-2]
	\arrow["f"', from=2-1, to=2-2]
\end{tikzcd}}\\~\\
where the top map is given by the projection to $E$. 
\end{prp}

Recall that we defined the mapping path space to be $$P_f=f^\ast(Y^I)=\{(x,\phi)\subseteq X\times Y^I\;|\;f(x)=\pi(\phi)=\phi(1)\}$$ where $\pi:Y^I\to Y$ is defined as $\pi(\phi)=\phi(1)$. We can factorize any continuous map into a fibration and a homotopy equivalence through the mapping path space. Because we are working with the mapping path space here, we need to restrict our attention to compactly generated space. 

\begin{thm}{}{} Let $f:X\to Y$ be a map with $Y$ compactly generated. Then $\pi:P_f\to Y$ defined by $\pi(x,\phi)=\phi(1)$ is a fibration. Moreover, there exists a homotopy equivalence $h:X\to P_f$ such that the following diagram commutes: \\~\\
\adjustbox{scale=1,center}{\begin{tikzcd}
	X && Y \\
	& {P_f}
	\arrow["f", from=1-1, to=1-3]
	\arrow["{\exists h}"', dashed, from=1-1, to=2-2]
	\arrow["\pi"', from=2-2, to=1-3]
\end{tikzcd}}
\end{thm}

\subsection{Cofibrations and The Homotopy Extension Property}
\begin{defn}{The Homotopy Extension Property}{} Let $i:A\to X$ be a map and let $Y$ be a space. Denote $i_0$ the inclusion map $A\times\{0\}\hookrightarrow A\times I$. We say that $i$ has the homotopy extension property with respect to $Y$ if for every homotopy $H:A\times I\to Y$ and every map $f:X\to Y$ such that $$H\circ i_0=f\circ i$$ there exists a homotopy $\widetilde{H}:X\times I\to Y$ such that the following diagram commute: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	{A\times\{0\}} && {A\times I} \\
	& Y \\
	{X\times\{0\}} && {X\times I}
	\arrow["{i_0}", hook, from=1-1, to=1-3]
	\arrow["i"', from=1-1, to=3-1]
	\arrow["H"', from=1-3, to=2-2]
	\arrow["{i\times\text{id}}", from=1-3, to=3-3]
	\arrow["f", from=3-1, to=2-2]
	\arrow[hook, from=3-1, to=3-3]
	\arrow["{\exists\widetilde{H}}"', dashed, from=3-3, to=2-2]
\end{tikzcd}}\\~\\
\end{defn}

The reason we had the entire digression on compactly generated spaces is because cofibrations can be redefined as a Eckmann-Hilton dual in the following form. 

\begin{lmm}{}{} Let $X,Y$ be compactly generated. Let $i:A\to X$ be a map and let $Y$ be a space. Denote $\pi_0:Y^I\to Y$ to be the map $(\gamma:I\to Y)\mapsto\gamma(0)$ Then $i$ has the homotopy extension property with respect to $Y$ if and only if for all maps $f:X\to Y$ and $F:A\to Y^I$, there exists a map $\widetilde{F}:X\to Y^I$ such that the following diagram commutes: \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	A & {Y^I} \\
	X & Y
	\arrow["F", from=1-1, to=1-2]
	\arrow["i"', from=1-1, to=2-1]
	\arrow["{\pi_0}", from=1-2, to=2-2]
	\arrow["{\widetilde{F}}"{description}, dashed, from=2-1, to=1-2]
	\arrow["f"', from=2-1, to=2-2]
\end{tikzcd}}\\~\\
\end{lmm}

\begin{defn}{Cofibrations}{} We say that a map $i:A\to X$ is a cofibration if it has the homotopy extension property for all spaces $Y$. 
\end{defn}

\begin{defn}{Pullbacks of a Cofibration}{} Let $i:A\to X$ be a cofibration and let $g:A\to C$ be a map. Define the pullback of $i$ by $g$ to be $$f_\ast(X)=\frac{X\amalg C}{i(a)\sim g(a)}$$ together with the inclusion map $i_f:X\to f_\ast(X)$. 
\end{defn}

\begin{prp}{}{} Let $i:A\to X$ be a cofibration and let $g:A\to C$ be a map. Then the map $C\to f^\ast(X)$ is a cofibration. Moreover, the following diagram commutes: \\~\\
\adjustbox{scale=1,center}{\begin{tikzcd}
	A & C \\
	X & {f_\ast(X)}
	\arrow["f", from=1-1, to=1-2]
	\arrow["i"', from=1-1, to=2-1]
	\arrow[from=1-2, to=2-2]
	\arrow["{i_f}"', from=2-1, to=2-2]
\end{tikzcd}}\\~\\
where the map $C\to f_\ast(X)$ is the inclusion map. 
\end{prp}

Dual to the factorization of the mapping path space, we can factorize a map into a homotopy equivalence and a cofibration through the mapping cylinder $$M_f=\frac{(X\times I)\amalg Y}{(x,0)\sim f(x)}=(X\times I)\amalg_fY$$

\begin{thm}{}{} Let $f:A\to X$ be a map. Then the inclusion map $i:A\to M_f$ defined by $i(a)=[a,0]$ is a cofibration. Moreover, there exists a homotopy equivalence $h:M_f\to X$ such that the following diagram commutes: \\~\\
\adjustbox{scale=1,center}{\begin{tikzcd}
	A && X \\
	& {M_f}
	\arrow["f", from=1-1, to=1-3]
	\arrow["i"', from=1-1, to=2-2]
	\arrow["{\exists h}"', dashed, from=2-2, to=1-3]
\end{tikzcd}}
\end{thm}

\subsection{Fibers and Cofibers}
\begin{defn}{Fibers of a Fibration}{} Let $p:E\to B$ be a fibration. Define the fiber of $p$ at $b\in B$ to be $$E_b=p^{-1}(b)$$
\end{defn}

The following definition is a supporting notion for our proof that fibers of a fibration are homotopy equivalent. 

\begin{defn}{Induced Map of Fibers}{} Let $p:E\to B$. Let $\gamma:I\to B$ be a path from $b_1$ to $b_2$. Define the induced map of fibers of $\gamma$ as follows: The map $H:E_{b_1}\times I\to B$ defined by $H(x,t)=\gamma(t)$ is a homotopy. Using the HLP of $p$, we obtain a lift: \\~\\
\adjustbox{scale=1,center}{\begin{tikzcd}
	{E_{b_1}\times\{0\}} & E \\
	{E_{b_1}\times I} & B
	\arrow["{\widetilde{H(-,0)}}", hook, from=1-1, to=1-2]
	\arrow[hook, from=1-1, to=2-1]
	\arrow["p", from=1-2, to=2-2]
	\arrow["{\widetilde{H}}"{description}, dashed, from=2-1, to=1-2]
	\arrow["H"', from=2-1, to=2-2]
\end{tikzcd}} \\~\\
Since $p\circ\widetilde{H}(x,t)=\gamma(t)$, we have that $\widetilde{H}(x,1)\in E_{b_2}$. The induced map of fibers is then the map $$L_\gamma:E_{b_1}\to E_{b_2}$$ defined by $L_\gamma=\widetilde{H(-,1)}$
\end{defn}

\begin{lmm}{}{} Let $p:E\to B$ be a fibration. Let $\gamma:I\to B$ be a path from $b_1$ to $b_2$. Then the following are true regarding $L_\gamma$. 
\begin{itemize}
\item If $\gamma\simeq\gamma'$ relative to boundary, then $L_\gamma\simeq L_{\gamma'}$.
\item If $\gamma:I\to B$ and $\gamma':I\to B$ are two composable paths, there is a homotopy equivalence $L_{\gamma\cdot\gamma'}\simeq L_{\gamma'}\circ L_\gamma$
\end{itemize} \tcbline
\begin{proof}
\begin{itemize}
\item Let $F:I\times I\to B$ be a homotopy equivalence from $\gamma$ to $\gamma'$. Now consider the map $G:E_{b_1}\times I\times I\to B$ defined by $G(x,s,t)=F(s,t)$. Notice that $G(x,s,0)=F(s,0)=\gamma(s)$ and $G(x,s,1)=F(s,1)=\gamma'(s)$. Thus, we proceed as above by lifting $G(x,s,0)$ and $G(x,s,1)$ to obtain respectively $\widetilde{G(x,s,0)}$ and $\widetilde{G(x,s,1)}$ for which $\widetilde{G(x,1,0)}=L_\gamma$ and $\widetilde{G(x,1,1)}=L_{\gamma'}$. Now define $K:E_{b_1}\times I\times\partial I\to E$ by $$K(x,s,t)=\begin{cases}
\widetilde{G(x,s,1)} & \text{ if } t=0\\
G(x,s,1) & \text{ if } t=1
\end{cases}$$ We now obtain a homotopy called $\widetilde{G}:E_{b_1}\times I\times I\to E$ by the homotopy lifting property: \\~\\
\adjustbox{scale=1,center}{\begin{tikzcd}
	{X\times I\times\partial I} & E \\
	{X\times I\times I} & B
	\arrow["K", from=1-1, to=1-2]
	\arrow[hook, from=1-1, to=2-1]
	\arrow["p", from=1-2, to=2-2]
	\arrow["\widetilde{G}"{description}, dashed, from=2-1, to=1-2]
	\arrow["G"', from=2-1, to=2-2]
\end{tikzcd}} \\~\\
Now $\tilde{G}(-,1,-):E_b\times I\to E$ is then a homotopy equivalence from $\widetilde{G}(x,1,0)=L_\gamma$ to $\widetilde{G}(x,1,1)=L_{\gamma'}$. 
\item We can repeat the above construction for $\gamma$ and $\gamma'$ to obtain homotopies $G:E_{b_1}\times I\to E$ and $G':E_{b_1}\times I\to E$ such that when $t=1$ we recover $\tilde{\gamma}$, $\tilde{\gamma'}$ and $\tilde{\gamma\cdot\gamma'}$ respectively. Now the composition of $G$ and $G'$ by traversing along $t\in I$ with twice the speed gives precisely a lift of $\gamma\cdot\gamma'$ (one can check the boundary conditions). Thus $L_{\gamma\cdot\gamma'}$ obtained in this manner coincides up to homotopy equivalence to $L_{\gamma'}\circ L_\gamma$ by invoking part a). 
\end{itemize}
\end{proof}
\end{lmm}

\begin{thm}{}{} Let $p:E\to B$ be a fibration. Let $b_1$ and $b_2$ lie in the same path component of $B$. Then there is a homotopy equivalence $$E_{b_1}\simeq E_{b_2}$$ given by the lift of any path $\gamma:I\to B$ from $b_1$ to $b_2$. \tcbline
\begin{proof}
Let $\gamma:I\to B$ be a path from $b_1$ to $b_2$. From the above, it follows that $L_{\overline{\gamma}}\circ L_\gamma\simeq\text{id}_{E_b}$ for any loop $\gamma:I\to B$ with basepoint $b$. We conclude that $L_\gamma$ is a homotopy equivalence and so the fibers of $p:E\to B$ are homotopy equivalent. 
\end{proof}
\end{thm}

\begin{defn}{Fiber of a Fibration}{} Let $p:E\to B$ be a fibration where $B$ is path connected. Define the fiber of $p$ to be a space $F$ such that each fiber $E_b$ for $b\in B$ is homotopy equivalent to. 
\end{defn}

\begin{defn}{Homotopy Fibers and Cofibers}{} Let $f:X\to Y$ be a map. Define the homotopy fiber of $f$ to be the mapping fiber $$F_f=\{(x,\phi)\in X\times Y^I\;|\;f(x)=\phi(1)\}$$ Define the homotopy cofiber of $f$ to be the mapping cone $$C_f=\frac{(X\times I)\amalg Y}{(x,1)\sim f(x),(x,0)\sim(x',0)}$$
\end{defn}

Note the difference between homotopy fibers and the mapping path space. The latter is defined by considering the fibration $\pi:X^I\to X$ where $\pi(\phi)=\phi(0)$. But homotopy fibers are defined the end point $\phi(1)$. In fact, this is the main ingredient in proving that this notion is homotopy equivalent to the usual notion of fibers. \\~\\

We have previously seen that the mapping fiber and the mapping cone of a map are dual notions in $\bold{Top}$. 

\begin{prp}{}{} Let $p:E\to B$ be a fibration. Then the homotopy fibers of $p$ are homotopy equivalent to the fibers of $p$. 
\end{prp}

\subsection{The Fiber and Cofiber Sequences}
\begin{defn}{Path Spaces}{} Let $(X,x_0)$ be a pointed space. Define the path space of $(X,x_0)$ to be $$PX=\{\phi:(I,0)\to(X,x_0)\;|\;\phi(0)=x_0\}=\text{Map}_\ast((I,0),(X,x_0))$$ together with the topology of the mapping space. 
\end{defn}

\begin{thm}{}{} Let $X$ be a space. Then the following are true. 
\begin{itemize}
\item The map $\pi:PX\to X$ defined by $\pi(\phi)=\phi(1)$ is a fibration with fiber $\Omega X$
\item The map $\pi:X^I\to X$ defined by $\pi(\phi)=\phi(1)$ is a fibration with fiber homeomorphic to $PX$. 
\end{itemize}
\end{thm}

We now write a fibration as a sequence $F\to E\to B$ for $F$ the fiber of the fibration $p:E\to B$. This compact notation allows the following theorem to be formulated nicely. 

\begin{thm}{}{} Let $f:X\to Y$ be a fibration with homotopy fiber $F_f$. Let $\iota:\Omega Y\to F_f$ be the inclusion map and $\pi:F_f\to X$ the projection map. Then up to homotopy equivalence of spaces, there is a sequence \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	\cdots & {\Omega^2 X} & {\Omega^2Y} & {\Omega F_f} & {\Omega X} & {\Omega_Y} & {F_f} & X & Y
	\arrow[from=1-1, to=1-2]
	\arrow["{\Omega^2 f}", from=1-2, to=1-3]
	\arrow["{-\Omega\iota}", from=1-3, to=1-4]
	\arrow["{-\Omega\pi}", from=1-4, to=1-5]
	\arrow["{-\Omega f}", from=1-5, to=1-6]
	\arrow["\iota", from=1-6, to=1-7]
	\arrow["\pi", from=1-7, to=1-8]
	\arrow["f", from=1-8, to=1-9]
\end{tikzcd}}\\~\\
where any two consecutive maps form a fibration. Moreover, $-\Omega f:\Omega X\to\Omega Y$ is defined as $$(-\Omega f)(\zeta)(t)=(f\circ\zeta)(1-t)$$ for $\zeta\in\Omega X$. 
\end{thm}

There is then the dual notion of loop spaces and the corresponding sequence. Write a cofibration $f:A\to X$ with homotopy cofiber $B$ as $B\to A\to X$. 

\begin{thm}{}{} Let $f:X\to Y$ be a cofibration with homotopy cofiber $C_f$. Let $i:Y\to C_f$ be the inclusion map and $\pi:C_f\to C_f/Y\cong\Sigma X$ be the projection map. Then up to homotopy equivalence of spaces, there is a sequence \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	X & Y & {C_f} & {\Sigma X} & {\Sigma Y} & {\Sigma C_f} & {\Sigma^2X} & {\Sigma^2Y} & \cdots
	\arrow["f", from=1-1, to=1-2]
	\arrow["i", from=1-2, to=1-3]
	\arrow["\pi", from=1-3, to=1-4]
	\arrow["{-\Sigma f}", from=1-4, to=1-5]
	\arrow["{-\Sigma i}", from=1-5, to=1-6]
	\arrow["{-\Sigma\pi}", from=1-6, to=1-7]
	\arrow["{\Sigma^2 f}", from=1-7, to=1-8]
	\arrow[from=1-8, to=1-9]
\end{tikzcd}}\\~\\
where any two consecutive maps form a cofibration. Moreover, $-\Sigma f:\Sigma X\to\Sigma Y$ is defined by $$(-\Sigma f)(x\wedge t)=f(x)\wedge(1-t)$$
\end{thm}

\begin{thm}{}{} Let $p:E\to B$ be a fibration over a path connected space $B$ with fiber $F$. Let $\iota:F\hookrightarrow E$ be the inclusion of the fiber. Then there is a long exact sequence in homotopy groups: \\~\\
\adjustbox{scale=0.75,center}{\begin{tikzcd}
	\cdots & {\pi_{n+1}(B,b_0)} & {\pi_n(F,e_0)} & {\pi_n(E,e_0)} & {\pi_n(B,b_0)} & {\pi_{n-1}(F,e_0)} & \cdots & {\pi_1(E,e_0)} & {\pi_1(B,b_0)}
	\arrow[from=1-1, to=1-2]
	\arrow["\partial", from=1-2, to=1-3]
	\arrow["{\iota_\ast}", from=1-3, to=1-4]
	\arrow["{p_\ast}", from=1-4, to=1-5]
	\arrow["\partial", from=1-5, to=1-6]
	\arrow[from=1-6, to=1-7]
	\arrow[from=1-7, to=1-8]
	\arrow["{p_\ast}", from=1-8, to=1-9]
\end{tikzcd}}\\~\\
for $e_0\in E$ and $b_0=p(e_0)$. Moreover, $p_\ast$ is an isomorphism. 
\end{thm}

\subsection{Serre Fibrations}
\begin{defn}{Serre Fibration}{} We say that a map $p:E\to B$ is a Serre fibration if it has the homotopy lifting property with respect to all CW-complexes. 
\end{defn}

\begin{lmm}{}{} Every (Hurewicz) fibration is a Serre fibration. \tcbline
\begin{proof}
This is true since Hurewicz fibrations satisfies the homotopy lifting property with respect to all topological spaces, including CW complexes. 
\end{proof}
\end{lmm}

\begin{prp}{}{} Let $p:E\to B$ be a fibration where $B$ is path connected. Let $F$ be the fiber of $p$. Let $b\in B$. Then the map $$\cdot:\pi_1(B)\times E_b\to E_b$$ defined by $[\gamma]\cdot x=L_\gamma(x)$ induces an action of $\pi_1(B)$ on the homology groups $H_\ast(F;G)$ given by $[\gamma]\cdot[z]=(L_\gamma)_\ast([z])$ for any $g\in G$. \tcbline
\begin{proof}
Notice first that such a map is well defined by lemma 6.3.3. Associativity follows from the second point of lemma 6.3.3. Identity follows the unique lift of the identity loop $e_b$ that gives $L_{e_b}$ is also the identity. 
\end{proof}
\end{prp}


\pagebreak
\section{Bonus?}
\subsection{Postnikov Towers}
\begin{defn}{Postnikov Towers}{} Let $X$ be a path connected space. A Postnikov tower is the following commutative diagram \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	& X \\
	\\
	\cdots & {X_n} & {X_{n-1}} & \cdots & {X_2} & {X_1} & \ast
	\arrow[from=1-2, to=3-2]
	\arrow[from=1-2, to=3-3]
	\arrow[from=1-2, to=3-5]
	\arrow[from=1-2, to=3-6]
	\arrow[from=3-1, to=3-2]
	\arrow["{p_n}"', from=3-2, to=3-3]
	\arrow[from=3-3, to=3-4]
	\arrow[from=3-4, to=3-5]
	\arrow["{p_2}"', from=3-5, to=3-6]
	\arrow["{p_1}"', from=3-6, to=3-7]
\end{tikzcd}}\\~\\
such that the following are true. 
\begin{itemize}
\item The maps $X\to X_n$ for each $n\in\N$ induces isomorphisms $\pi_i(X)\cong\pi_i(X_n)$ for $i\leq n$. 
\item $\pi_i(X_n)$ for $i>n$. 
\item Each $p_n:X_n\to X_{n-1}$ for $n\in\N$ is a fibration with fiber $K(\pi_n(X),n)$. 
\end{itemize}
\end{defn}

\begin{thm}{}{} Suppose that there is an inverse system of spaces \\~\\
\adjustbox{scale=1.0,center}{\begin{tikzcd}
	& \lim_{n\to\infty}X_n \\
	\\
	\cdots & {X_n} & {X_{n-1}} & \cdots & {X_2} & {X_1} & \ast
	\arrow[from=1-2, to=3-2]
	\arrow[from=1-2, to=3-3]
	\arrow[from=1-2, to=3-5]
	\arrow[from=1-2, to=3-6]
	\arrow[from=3-1, to=3-2]
	\arrow["{p_n}"', from=3-2, to=3-3]
	\arrow[from=3-3, to=3-4]
	\arrow[from=3-4, to=3-5]
	\arrow["{p_2}"', from=3-5, to=3-6]
	\arrow["{p_1}"', from=3-6, to=3-7]
\end{tikzcd}}\\~\\
The functor $\pi_i$ for $i\in\N$ induces a cone in $\bold{Grp}$. By definition of $\lim_{\leftarrow}\pi_i(X_n)$, there is a unique map $$\lambda:\pi_i\left(\lim_{\leftarrow}X_n\right)\to\lim_{\leftarrow}\pi_i(X_n)$$ Then the following are true regarding $\lambda$. 
\begin{itemize}
\item $\lambda$ is surjective
\item $\lambda$ is injective if the maps $\pi_{i+1}(X_n)\to\pi_{i+1}(X_{n-1})$ are surjective for sufficient large $n$. 
\end{itemize}
\end{thm}

\begin{prp}{}{} Let $X$ be a connected CW complex. Then there exists a Postnikov tower for $X$. 
\end{prp}

\begin{prp}{}{} Let $X$ be a connected CW complex. Choose a Postnikov tower of $X$. Then there is a weak homotopy equivalence $$X\simeq\lim_{\leftarrow}X_n$$ so that $X$ is a CW approximation of $\lim_{\leftarrow}X_n$. 
\end{prp}








\end{document}
